---
title: "Untitled"
author: "Victor Møller"
date: "20 maj 2019"
output: html_document
---

updated 09-11-2019.
Still much work to do. 

```{r}

library(pacman)
p_load(readr, tidyverse, ggplot2, RColorBrewer, reshape2, ggthemes,
       viridis, ggridges, ggunchained, rlang, cowplot)

```

Preprocessing (should also be adjusted to accommodate better early prep). 

```{r}

#load data 
setwd("~/CRUST-1/MetascienceBA/data/dataPlotting")
violin <- read_csv("violin_extended_MetascienceBA.csv")
violinstrat <- read_csv("violin_extended_bystrat_MetascienceBA.csv")

violin <- violin %>%
  mutate(network = factor(network),
        population = factor(population),
        sigma = factor(sigma),
        colab_cond = factor(colab_cond),
        net_size = factor(net_size),
        true_model = factor(true_model),
        strategy = factor("overall"),
        colab_cond = recode(colab_cond,
                               NOLAB = "No",
                               COLAB = "Yes"))

violinstrat <- violinstrat %>%
  mutate(network = factor(network),
        population = factor(population),
        sigma = factor(sigma),
        colab_cond = factor(colab_cond),
        net_size = factor(net_size),
        true_model = factor(true_model),
        strategy = factor(strategy),
        colab_cond = recode(colab_cond,
                               NOLAB = "No",
                               COLAB = "Yes"))

df <- rbind(violin, violinstrat)
```

raincloud prep

```{r}

#preparing raincloud (can be customized)
raincloud_theme = theme(
text = element_text(size = 10),
axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 16),
axis.text = element_text(size = 14),
axis.text.x = element_text(vjust = 0.5),
legend.title=element_text(size=16),
legend.text=element_text(size=16),
legend.position = "right",
plot.title = element_text(lineheight=.8, face="bold", size = 16),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

```

new directory & loading flatViolin

```{r}

setwd("~/CRUST-1")
baseDir <- "."
scriptDir <- paste0(baseDir, "/FunctionsLoads/Functions")
#inputDir <- paste0(baseDir, "/data")
#outputDir <- paste0(baseDir, "/data")
source(paste0(scriptDir, "/flatViolin.R"))


```

Main effects within conditions (function)
Just RR. 

This plot is not used in the paper as it is very messy 
(multiple distributions) & also the populations don't differ much. 

```{r}

#raincloud plot

RR_FUN <- function(.df, .xvar, .strat, .colab, .net1, .net2){
  
  xvar <- enquo(.xvar)
  strat <- enquo(.strat)
  colab <- enquo(.colab)
  net1 <- enquo(.net1)
  net2 <- enquo(.net2)
  
g <- .df %>%
  filter(strategy == UQ(strat),
         colab_cond == UQ(colab),
         network == UQ(net1) | network == UQ(net2)) %>%
  ggplot(aes(x = UQ(xvar), 
             y = RR, fill = UQ(xvar))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = RR, color = UQ(xvar)), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(x = "Populations", 
       y = "Replication Rate", 
       color = "Proportion of different models", 
       title = "Replication rate",
       subtitle = paste0("Networks: ", quo_name(net1), " & ",
                         quo_name(net2), " | ",
                         "Colab: ", quo_name(colab))) +
  raincloud_theme

#call the plot
g

}


```

Running the function: 

```{r}

#population & different conditions. 
p1 <- RR_FUN(df, population, "overall", "No", "Small", "Lattice")
p2 <- RR_FUN(df, population, "overall", "Yes", "Small", "Lattice")
p3 <- RR_FUN(df, population, "overall", "Yes", "PT", "TOM")

plot_grid(p1, p2, p3)

```

Prep for next section (between conditions).

```{r}

df_subsets <- df %>%
  filter(!((network == "PT" | network == "TOM") & colab_cond == "No")) %>%
  mutate(condition = ifelse((network == "Lattice" |
                            network == "Small") &
                            colab_cond == "No", 
                            "Small & Lattice, Colab: No",
                            ifelse((network == "Lattice" |
                                   network == "Small") &
                                   colab_cond == "Yes", 
                                   "Small & Lattice, Colab: Yes",
                                   "Citation Networks, Colab: Yes")),
         condition = factor(condition))


```

Effects between conditions. 

Also, this plot is not used in the paper as it is very messy
(multiple distributions) & no clear differences. 

```{r}

#raincloud plot

RR_FUN <- function(.df, .var1, .var2, .strat){
  
  var1 <- enquo(.var1)
  var2 <- enquo(.var2)
  strat <- enquo(.strat)
  
g <- .df %>%
  filter(strategy == UQ(strat)) %>%
  ggplot(aes(x = UQ(var1), y = RR, fill = UQ(var2))) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = RR, color = UQ(var2)), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    #coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var2)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var2))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g


#call the plot
g

}

colnames(df_subsets)
RR_FUN(df_subsets, condition, population, "overall")
RR_FUN(df_subsets, condition, sigma, "overall")
RR_FUN(df_subsets, condition, true_model, "overall")


```

RR by strategies. 

Neighbor sampling & Colab gives higher replication rate 
than "research" strategy, but we don't use this as of now. 

```{r}
#raincloud plot

RR_FUN <- function(.df, .var1, .var2, .strat){
  
  var1 <- enquo(.var1)
  var2 <- enquo(.var2)
  strat <- enquo(.strat)
  
g <- .df %>%
  filter(strategy != UQ(strat)) %>%
  ggplot(aes(x = UQ(var1), y = RR, fill = UQ(var2))) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = RR, color = UQ(var2)), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    #coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var2)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var2))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g


#call the plot
g


}

colnames(df_subsets)
RR_FUN(df_subsets, condition, strategy, "overall")
```

RR by true / false (prep). 

```{r}

#read TF. 
TF <- read_csv("violin_ridges_TF_MetascienceBA.csv")

#prep TF. 
TF <- TF %>%
  filter(prop_t_mod == 1) %>%
  mutate(network = factor(network),
        population = factor(population),
        sigma = factor(sigma),
        colab_cond = factor(colab_cond),
        net_size = factor(net_size),
        true_model = factor(true_model),
        strategy = factor("overall"),
        colab_cond = recode(colab_cond,
                               NOLAB = "No",
                               COLAB = "Yes"),
        prop_t_mod = "True")

violin <- violin %>%
  mutate(prop_t_mod = "Overall")

RR_TF <- rbind(TF, violin)
RR_TF <- RR_TF %>%
  mutate(prop_t_mod = factor(prop_t_mod))

RR_TF_SUB <- RR_TF %>%
  filter(!((network == "PT" | network == "TOM") & colab_cond == "No")) %>%
  mutate(condition = ifelse((network == "Lattice" |
                            network == "Small") &
                            colab_cond == "No", 
                            "Small & Lattice, Colab: No",
                            ifelse((network == "Lattice" |
                                   network == "Small") &
                                   colab_cond == "Yes", 
                                   "Small & Lattice, Colab: Yes",
                                   "Citation Networks, Colab: Yes")),
         condition = factor(condition))

```

RR by true / false.

We don't use this as of now as it looks TERRIBLE.
We have way to few cases of "true" replication which
makes the picture very murky. 

```{r}

#raincloud plot

RR_FUN <- function(.df, .var1, .var2){
  
  var1 <- enquo(.var1)
  var2 <- enquo(.var2)
  
g <- .df %>%
  ggplot(aes(x = UQ(var1), y = RR, fill = UQ(var2))) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = RR, color = UQ(var2)), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    #coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var2)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var2))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g


#call the plot
g

}

colnames(df_subsets)
RR_FUN(RR_TF_SUB, condition, prop_t_mod)
RR_FUN(df_subsets, condition, sigma, "overall")
RR_FUN(df_subsets, condition, true_model, "overall")

```


RR & TAT (prep).
Again, we don't use this in the paper. 
It is quite messy without grouping over true models,
however, it does give a clear picture. 
We prefer to group by true models as well to
make it more clear. 

```{r}
setwd("~/CRUST-1/MetascienceBA/data/dataPlotting")
RR <- read_csv("violin_ridges_RR_MetascienceBA.csv")

#prep TF. 
RR <- RR %>%
  mutate(network = factor(network),
        population = factor(population),
        sigma = factor(sigma),
        colab_cond = factor(colab_cond),
        net_size = factor(net_size),
        true_model = factor(true_model),
        colab_cond = recode(colab_cond,
                               NOLAB = "No",
                               COLAB = "Yes"))

#by conditions 
RR_SUB <- RR %>%
  filter(!((network == "PT" | network == "TOM") & colab_cond == "No")) %>%
  mutate(condition = ifelse((network == "Lattice" |
                            network == "Small") &
                            colab_cond == "No", 
                            "Small & Lattice, Colab: No",
                            ifelse((network == "Lattice" |
                                   network == "Small") &
                                   colab_cond == "Yes", 
                                   "Small & Lattice, Colab: Yes",
                                   "Citation Networks, Colab: Yes")),
         condition = factor(condition))

#melting
melt_RR_TAT <- melt(RR_SUB, 
                    id.vars = c("replica", "population",
                                "sigma", "true_model", 
                                "colab_cond", "condition"), 
                    measure.vars = c("RR", "TAT"), 
                    variable.name = "variable", 
                    value.name = "proportion")

```

overall RR vs. TAT

```{r}
#raincloud plot

RR_FUN <- function(.df, .var1){
  
  var1 <- enquo(.var1)
  
g <- .df %>%
  ggplot(aes(x = UQ(var1), y = proportion, fill = variable)) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = proportion, color = variable), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    #coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var1)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var1))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g


#call the plot
g

}

colnames(df_subsets)
RR_FUN(melt_RR_TAT, condition)
RR_FUN(melt_RR_TAT, sigma)
```

RR vs. TAT (with filter).
Again, we don't use this even though it is quite cool.
We prefer to group these three plots into one,
while not grouping over condition. 

```{r}

RR_FUN <- function(.df, .var1, .sigma, .true){
  
  var1 <- enquo(.var1)
  sigma <- enquo(.sigma)
  true <- enquo(.true)
  
g <- .df %>%
  filter(sigma == UQ(sigma),
         true_model == UQ(true)) %>%
  ggplot(aes(x = UQ(var1), y = proportion, fill = variable)) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = proportion, color = variable), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    #coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var1)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var1))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g


#call the plot
g

}

colnames(df_subsets)
RR_FUN(melt_RR_TAT, condition, 0.5, 7)
RR_FUN(melt_RR_TAT, condition, 0.5, 13)
RR_FUN(melt_RR_TAT, condition, 0.5, 2)
```

The plot we use. 
RR & TAT for true models. 
Hard-set Colab, networks & true model.

PREP

```{r}
melt_RR_TAT <- melt(RR, 
                    id.vars = c("replica", "network",
                                "population", "sigma", "true_model", 
                                "colab_cond"), 
                    measure.vars = c("RR", "TAT"), 
                    variable.name = "variable", 
                    value.name = "proportion")
```


```{r}

RR_FUN <- function(.df, .var1, .sigma, .net1, .net2, .colab){
  
  var1 <- enquo(.var1)
  sigma <- enquo(.sigma)
  net1 <- enquo(.net1)
  net2 <- enquo(.net2)
  colab <- enquo(.colab)
  
g <- .df %>%
  filter(sigma == UQ(sigma),
         colab_cond == UQ(colab),
         network == UQ(net1) | network == UQ(net2)) %>%
  ggplot(aes(x = UQ(var1), y = proportion, fill = variable)) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = proportion, color = variable), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    #coord_flip() +
    theme_bw() +
    labs(x = "True models", 
       y = "RR & TAT", 
       fill = "Measure", 
       titles = "RR & TAT for true models",
       subtitle = paste0("Colab: ", quo_name(colab), " | ",
                         "Sigma: ", quo_name(sigma), " | ", 
                        "Networks: ", quo_name(net1), " & ",
                         quo_name(net2))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g


#call the plot
g

}

colnames(df_subsets)
RR_FUN(melt_RR_TAT, true_model, 0.5, "Small", "Lattice", "Yes")

```

The same with Ridges

```{r}

RR_FUN <- function(.df, .var1, .sigma, .net1, .net2, .colab){
  
  var1 <- enquo(.var1)
  sigma <- enquo(.sigma)
  net1 <- enquo(.net1)
  net2 <- enquo(.net2)
  colab <- enquo(.colab)

  g <- .df %>%
      filter(sigma == UQ(sigma),
         colab_cond == UQ(colab),
         network == UQ(net1) | network == UQ(net2)) %>%
      ggplot(aes(x = proportion,
                 y = UQ(var1), 
                 color = variable,
                 fill = variable)) +
      geom_density_ridges(jittered_points = TRUE, scale = 0.8, 
                          rel_min_height = .01,
                          point_shape = "|", point_size = 3, size = 0.25, 
                          position = position_points_jitter(height = 0)) +
      scale_y_discrete(expand = c(0.01, 0)) +
      scale_x_continuous(expand = c(0,0), 
                         name = "Replication rate & time at true model") +
      scale_fill_manual(values = c("#D55E0050", "#0072B250"), 
                        labels = c("Replication rate", "Time at true model")) +
      scale_color_manual(values = c("#D55E00", "#0072B2"), guide = "none") +
      scale_discrete_manual("point_color", values = c("#D55E00", "#0072B2"), 
                            guide = "none") +
      guides(fill = guide_legend("",
        override.aes = list(
        fill = c("#D55E00A0", "#0072B2A0"),
        color = NA, point_color = NA))
      ) +
      theme_ridges(center = TRUE) + 
      theme_janco_point() 
      
    g + labs(caption = "Sample size: 100. 'Replication rate' and 'proportion of time at the true model' both on the x-axis. \n Density curves are averaged over sigma-levels, true models and replicas. \n Lines at the bottom represent mean values for individual replicas") +
      theme(plot.caption = element_text(hjust = 0.5))
}

RR_FUN(melt_RR_TAT, true_model, 0.5, "Small", "Lattice", "Yes")
```




We don't use the below for now:: 
################################

Main effects (2). 
Flipped plot of main effects avg. over all other grouping variables. 
NB: same as above (fix this). 

```{r}

#raincloud plot

RR_FUN2 <- function(df, .var){
  
  var <- enquo(.var)

g <- df %>%
  ggplot(aes(x = UQ(var), 
             y = RR, fill = UQ(var))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = RR, color = UQ(var)), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  coord_flip() +
  theme_bw() +
  labs(title = paste0("Replication rate for ", as_label(var), "s"), #with s?
       subtitle = "Averaged over all other grouping variables",
       x = paste0(as_label(var), "s"), #with s?
       y = "Replication rate") +
  raincloud_theme

#call the plot
g

}

#running the function 
colnames(df_RR)
RR_FUN2(df_RR, population)
RR_FUN2(df_RR, sigma)
RR_FUN2(df_RR, network)
RR_FUN2(df_RR, true_model) #looks terrible
RR_FUN2(df_RR, colab_cond) #looks terrible 
RR_FUN2(df_RR, net_size)

```

Interaction effects (1). 
Upright plot of two main effects (possibly interaction)
avg. over all other grouping variables. 
Some of these look terrible bc. we have terrible var names. 
Maybe just hard-code once we have found the plots we want to present. 
Still only NOLAB. 

```{r}

RR_FUN3 <- function(.df, .var1, .var2){
  
  var1 <- enquo(.var1)
  var2 <- enquo(.var2)
  
#raincloud plot
  g <- .df %>%
    filter(strategy == "overall",
         colab_cond == "No") %>%
    ggplot(aes(x = UQ(var1), y = RR, fill = UQ(var2))) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = RR, color = UQ(var2)), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    #coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var2)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var2))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g

}

#what can we plot over? 
colnames(df)

#population vs. everything: 
RR_FUN3(df, population, network) #tom is lower for all. 
RR_FUN3(df, population, sigma) #some interaction w. BO vs. everyone else. 
RR_FUN3(df, population, true_model) #no real effect. 
RR_FUN3(df, population, net_size) #no effect. 

#network vs. everything 
RR_FUN3(df, network, population) #TOM does worst overall. 
RR_FUN3(df, network, sigma) #TOM does worst overall 
RR_FUN3(df, network, true_model) #TOM does worst overall. 
RR_FUN3(df, network, net_size) #same. 

#sigma vs. everything
RR_FUN3(df, sigma, network) #TOM worst, more spread for 0.2
RR_FUN3(df, sigma, population) #big Tess & Bo effects (unsurprisingly)
RR_FUN3(df, sigma, true_model) #very funky plot (weird interactions). 
RR_FUN3(df, sigma, net_size) #nothing. 

#true model vs. everything 
RR_FUN3(df, true_model, population)  
RR_FUN3(df, true_model, network) #least action/change/diff in TOM
RR_FUN3(df, true_model, sigma) #interaction effect (same as before)
RR_FUN3(df, true_model, net_size) #nothing. 

```

Interaction effects (2). 
Flipped plot of two main effects (possibly interaction)
avg. over all other grouping variables. 

```{r}

RR_FUN4 <- function(.df, .var1, .var2){
  
  var1 <- enquo(.var1)
  var2 <- enquo(.var2)
  
#raincloud plot
  g <- .df %>%
    ggplot(aes(x = UQ(var1), y = RR, fill = UQ(var2))) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = RR, color = UQ(var2)), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var2)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var2))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g

}

#what can we plot over? 
colnames(df_RR)

#population vs. everything: 
RR_FUN4(df_RR, population, network) #tom is lower for all. 
RR_FUN4(df_RR, population, sigma) #some interaction w. BO vs. everyone else. 
RR_FUN4(df_RR, population, true_model) #no real effect. 
RR_FUN4(df_RR, population, colab_cond) #no effect it seems. 

#network vs. everything 
RR_FUN4(df_RR, network, population) #TOM does worst overall. 
RR_FUN4(df_RR, network, sigma) #TOM does worst overall 
RR_FUN4(df_RR, network, true_model) #TOM does worst overall. 
RR_FUN4(df_RR, network, colab_cond) #TOM does worst overall. 

#sigma vs. everything
RR_FUN4(df_RR, sigma, network) #TOM worst, more spread for 0.2
RR_FUN4(df_RR, sigma, population) #big Tess & Bo effects (unsurprisingly)
RR_FUN4(df_RR, sigma, true_model) #interaction effect for sure. 
RR_FUN4(df_RR, sigma, colab_cond) #nothing. 

#true model vs. everything 
RR_FUN4(df_RR, true_model, population)  
RR_FUN4(df_RR, true_model, network) #least action/change/diff in TOM
RR_FUN4(df_RR, true_model, sigma) #interaction effect (same as before)
RR_FUN4(df_RR, true_model, colab_cond) #nothing

#colab condition vs. everything
RR_FUN4(df_RR, colab_cond, network) #nothing
RR_FUN4(df_RR, colab_cond, population) #nothing.
RR_FUN4(df_RR, colab_cond, sigma) #nothing.
RR_FUN4(df_RR, colab_cond, true_model) #nothing. 

```

Potentially create chunk for plots based on true/false replication

------------------

Research strategy: 

```{r}
#raincloud plot

RR_FUN5 <- function(df, .var){
  
  var <- enquo(.var)

g <- df %>%
  filter(colab_cond == "NOLAB") %>%
  ggplot(aes(x = UQ(var), 
             y = RR, fill = UQ(var))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = RR, color = UQ(var)), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = paste0("Replication rate for ", as_label(var), "s"), #with s?
       subtitle = "Averaged over all other grouping variables",
       x = paste0(as_label(var), "s"), #with s?
       y = "Replication rate") +
  raincloud_theme

#call the plot
g

}

#running the function 
colnames(df)
RR_FUN5(df, strategy)

```

```{r}
#raincloud plot

RR_FUN6 <- function(df, .var){
  
  var <- enquo(.var)

g <- df %>%
  filter(strategy == "overall") %>%
  ggplot(aes(x = UQ(var), 
             y = RR, fill = UQ(var))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = RR, color = UQ(var)), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = paste0("Replication rate for ", as_label(var), "s"), #with s?
       subtitle = "Averaged over all other grouping variables",
       x = paste0(as_label(var), "s"), #with s?
       y = "Replication rate") +
  raincloud_theme

#call the plot
g

}

#running the function 
colnames(df)
RR_FUN6(df, colab_cond)
RR_FUN6(df, sigma)


```

COLAB interactions

```{r}
#raincloud plot

RR_FUN7 <- function(.df, .var1, .var2){
  
  var1 <- enquo(.var1)
  var2 <- enquo(.var2)
  
#raincloud plot
  g <- .df %>%
    ggplot(aes(x = UQ(var1), y = RR, fill = UQ(var2))) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = RR, color = UQ(var2)), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    #coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var2)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var2))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g

}

#what can we plot over? 
colnames(df)

#population vs. everything: 
RR_FUN7(df, population, colab_cond)
RR_FUN7(df, sigma, colab_cond)
RR_FUN7(df, network, colab_cond)
RR_FUN7(df, true_model, colab_cond)
RR_FUN7(df, colab_cond, strategy)

```


sigma 100 

```{r}

#sigma as factor
small_RR$sigma <- as.factor(small_RR$sigma)

#raincloud plot
g <- small_RR %>%
  filter(sample_size == "100") %>%
  ggplot(aes(x = population, 
                              y = RR, fill = sigma)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
  geom_point(aes(y = RR, color = sigma), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) + #not clear that this changes much. 
  #guides(fill = FALSE) + #legend can be deleted. 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate by population",
       subtitle = "Sample size: 100", 
       x = "Population", 
       y = "Replication rate",
       fill = "Sigma") + #sets the legend title.
  raincloud_theme

#call the plot
g

```

for sample size 20

```{r}

#raincloud plot
g1 <- small_RR %>%
  filter(sample_size == "20") %>%
  ggplot(aes(x = population, 
                              y = RR, fill = sigma)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
  geom_point(aes(y = RR, color = sigma), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) + #not clear that this changes much. 
  #guides(fill = FALSE) + #legend can be deleted. 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate by population",
       subtitle = "Sample size: 20", 
       x = "Population", 
       y = "Replication rate",
       fill = "Sigma") + #sets the legend title.
  raincloud_theme

#call the plot
g1

library(cowplot)
plot_grid(g, g1)

```

