---
title: "prep_BA_reworkLOOP"
author: "Victor Møller"
date: "November 14, 2019"
output: html_document
---
30-11
This document tests & cleans data from ABM5. 
It is probably only going to work for test-phase with small
amounts of data. It takes data from "new_data" folder and outputs to "tests".


```{r}

#packages
library(pacman)
p_load(tidyverse, tidyselect, data.table)

#Naming scheme:
naming_scheme <- "_Devezer_fixed.csv"

```


```{r}
setwd("D:/data/Raw data from Computer Room/30-11/raw")

all_AIC <- read_csv("All_0.2_AIC_hard_100_2.csv")
all_BIC <- read_csv("All_0.2_BIC_hard_20_2.csv")

all <- rbind(all_AIC, all_BIC)

#THING TO CHANGE:
#timestep <- turn
#tmodel <- true_model
#initial_global_model <- old_gModel

#THINGS TO ADD:
#network <- None
#net_size <- None

#MORE FUNDAMENTALLY:
#strategy <- change all the 1,2,3,4,5 into agent names
#replicated <- just keep in mind that we don't do need to calculate anything 

#REY <- 1
#TESS <- 2
#BO <- 3
#MAVE <- 4

all <- all %>%
  rename(turn = timestep,
         true_model = tmodel,
         old_model = initial_global_model,
         modelCompare = modelcompare,
         orig_type = strategy,
         init_g_true = initial_global_true_model,
         prop_t_mod = selected_true_model,
         final_g_true = final_global_true_model) %>%
  mutate(network = factor("None"),
         net_size = factor("None"),
         colab_cond = factor("NOLAB"),
         studies = turn,
         orig_type = factor(orig_type, labels = c("Rey", "Tess", "Bo", "Mave")),
         modelCompare = factor(if_else(modelCompare == 4, "AIC", "BIC"))) %>%
  select(replica, turn, studies, population, sigma, network, net_size, 
         colab_cond, sample_size, true_model, modelCompare, orig_type, selected_model, 
         prop_t_mod, old_model, init_g_true, final_global_model, final_g_true, replicated)


df_basic <- all %>%
        group_by(replica, network, population, sigma, true_model) %>%
        summarize(RR = sum(replicated) / n())

RR_TAT <- all %>%
    group_by(replica, network, population, sigma, true_model) %>%
    summarize(RR = sum(replicated) / n(),
              TAT = 100 * (sum(as.numeric(final_global_model == true_model)) / n()))

tommy <- all %>%
      filter(prop_t_mod == 0) %>%
      group_by(replica, sigma, population, network, true_model,
           net_size, colab_cond) %>%
      summarize(agent_away = sum(as.numeric(init_g_true == 1 & 
                                        final_g_true == 0)),
            agent_total = sum(as.numeric(init_g_true == 1)))

TAT <- all %>%  
  group_by(replica, network, population, true_model, sigma, sample_size) %>% 
      mutate(TAT = 100 * (sum(as.numeric(final_global_model == true_model)) / n()),
        TAT_50 = ifelse(TAT >= 50, 1, 0)) %>%
      summarise(TAT = mean(TAT),
                TAT50 = mean(TAT_50)) 

TAT_AVG <- all %>%  
      group_by(network, population, true_model, sigma, sample_size) %>% 
      mutate(TAT = 100 * (sum(as.numeric(final_global_model == true_model)) / n()),
        TAT_50 = ifelse(TAT >= 50, 1, 0)) %>%
      summarise(TAT = mean(TAT),
                TAT50 = mean(TAT_50))

 df <- all %>%
        group_by(replica, population, network, sigma, true_model) %>% 
        summarize(first_row = min(which(final_g_true > init_g_true)))

```

rename and mutate variables

```{r}
#Working directory of RAW data. 
setwd("D:/data/Raw data from Computer Room/30-11/raw")

#your files 
files = list.files(pattern=c("*.csv"), full.names=TRUE)

#the function
data_rename <- function(i){
  
  for(i in files){
  
  #where your raw files are:   
  setwd("D:/data/Raw data from Computer Room/30-11/raw")
    
  #reading data:
  data <- read_csv(i)
  data <- na.omit(data)
  data <- tibble::as_tibble(data)
  
  #factorizing (might not work anyways): 
  data <- data %>%
  rename(turn = timestep,
         true_model = tmodel,
         old_model = initial_global_model,
         modelCompare = modelcompare,
         orig_type = strategy,
         init_g_true = initial_global_true_model,
         prop_t_mod = selected_true_model,
         final_g_true = final_global_true_model) %>%
  mutate(network = factor("None"),
         net_size = factor("None"),
         colab_cond = factor("NOLAB"),
         studies = turn,
         orig_type = factor(orig_type, labels = c("Rey", "Tess", "Bo", "Mave")),
         modelCompare = factor(if_else(modelCompare == 4, "AIC", "BIC"))) %>%
  select(replica, turn, studies, population, sigma, network, net_size, 
         colab_cond, sample_size, true_model, modelCompare, orig_type, selected_model, 
         prop_t_mod, old_model, init_g_true, final_global_model, final_g_true, replicated)
  
  #directory for the files: 
  setwd("D:/data/data_prepped_30-11")
  
  #write csv:
  write_csv(data, paste0(i))
  
  }
}

data_rename(files)
```

do we have all files.

```{r}

#Working directory of RAW data. 
setwd("D:/data/data_prepped_30-11")

#which files do we have
files = list.files(pattern=c("*.csv"), full.names=TRUE)

#do we lack anything 

#networks
identifiers <- c( 
              "Mave_", "Tess_", "All_", "Bo_", "Rey_",
              "_0.2_", "_0.5_", "_0.8_", 
              "_AIC_", "_BIC_",
              "_20_", "_100_",
              "_2.csv", "_7.csv", "_13.csv")

for (i in identifiers){
  
network <- noquote(i)

#quick check: 
x <- files
network <- str_detect(files, i)
subset <- x[network]
value <- length(unlist(subset))
print(paste0(value, ": ", i))

}


```

data preparation for "violin_extended_rework": 

```{r}

#working directory. 
setwd("D:/data/data_prepped_30-11")
path = "D:/data/data_prepped_30-11"
files <- list.files(path = path, pattern="*.csv")


#initializing empty list 
datalist <- list()

violin_extended_rework <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
            "turn", 
            "studies", 
            "network", 
            "population", 
            "sigma",
            "true_model",
            "replicated",
            "prop_t_mod")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          true_model = factor(true_model))
    
    #create DF. 
    df_basic <- df %>%
        group_by(replica, network, population, sigma, true_model) %>%
        summarize(RR = sum(replicated) / n()) 
    
    datalist[i] <- list(df_basic)

  }
    
  df <- do.call("rbind", datalist)
  
  #directory for the files: 
  setwd("D:/data/data_plotting")
  
  #write csv:
  write_csv(df, paste0("violin_extended", naming_scheme))

}

#calling the function
violin_extended_rework(files)

```

data preparation for "violin_ridges_rework":

```{r}

    #create DF.
    #working directory.
setwd("D:/data/data_prepped_30-11")
path = "D:/data/data_prepped_30-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list
datalist1 <- list()
datalist2 <- list()

violin_ridges_rework <- function(files){
 
  #selecting cols (check )
    mycols <- c("replica", 
            "turn", #need this??
            "studies", 
            "network", 
            "population", 
            "sigma",
            "true_model",
            "final_g_model",
            "prop_t_mod") #importantly. 
 
  for(i in files){

    #read csv
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          true_model = factor(true_model))
    
    #replication rate & TAT overall
    RR_TAT <- df %>%
    group_by(replica, network, population, sigma, true_model) %>%
    summarize(RR = sum(replicated) / n(),
              TAT = 100 * (sum(as.numeric(final_global_model == true_model)) / n())) 

    #replication rate & TAT (for )
    #legit to compute TAT for the subset?
    RR_TAT_TF <- df %>%
    group_by(prop_t_mod, replica, network, population, sigma, true_model) %>%
    summarize(RR = sum(replicated) / n(),
              TAT = 100 * (sum(as.numeric(final_global_model == true_model)) / n()))
    
    
    datalist1[i] <- list(RR_TAT)
    datalist2[i] <- list(RR_TAT_TF)
  }
    
  RR_TAT <- do.call("rbind", datalist1)
  RR_TAT_TF <- do.call("rbind", datalist2)

 
  #directory for the files:
  setwd("D:/data/data_plotting")
 
  #write csv:
  write_csv(RR_TAT, paste0("violin_ridges_RR", naming_scheme))
  write_csv(RR_TAT_TF, paste0("violin_ridges_TF", naming_scheme))

}

#calling the function
violin_ridges_rework(files)

```

### NOT INCLUDING TRUE_FALSE RIGHT NOW - As we're not dealing with proportions, the plots doesn't make any sense. Something akin to that could be made. 

###OUTCOME MEASURES:
____________________
Data prep for "Stickiness":

```{r}
#working directory. 
setwd("D:/data/data_prepped_30-11")
path = "D:/data/data_prepped_30-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list 
datalist <- list()

stickiness_rework <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
                "network", 
                "population", 
                "sigma",
                "true_model",
                "prop_t_mod", #proposed true? (1 = yes, 0 = no). 
                "init_g_true", #count of true orig. (testing) agents.
                "final_g_true")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          true_model = factor(true_model))
    
    #create DF
    df <- df %>%
      filter(prop_t_mod == 0) %>%
      group_by(replica, sigma, population, network, true_model) %>%
      summarize(agent_away = sum(as.numeric(init_g_true == 1 & 
                                        final_g_true == 0)),
            agent_total = sum(as.numeric(init_g_true == 1)))
    
    datalist[i] <- list(df)
  }
    
  df_final <- do.call("rbind", datalist)
  
  #directory for the files: 
  setwd("D:/data/data_outcome_measures")
  
  #write csv:
  write_csv(df_final, paste0("stickiness_rework", naming_scheme))

}

#calling the function
stickiness_rework(files)
```

Data prep for TAT_TAT50_rework.Rmd 

```{r}

#working directory. 
setwd("D:/data/data_prepped_30-11")
path = "D:/data/data_prepped_30-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list 
datalist1 <- list()
datalist2 <- list()

TAT50 <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
                "network", 
                "population", 
                "sigma",
                "true_model",
                "base_SS")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          true_model = factor(true_model))
    
    #TAT PER REPLICA
    TAT <- df %>%  
      group_by(replica, network, population, true_model, sigma, sample_size) %>% 
      mutate(TAT = 100 * (sum(as.numeric(final_global_model == true_model)) / n()),
        TAT_50 = ifelse(TAT >= 50, 1, 0)) %>%
      summarise(TAT = mean(TAT),
                TAT50 = mean(TAT_50)) 
        
    #TAT AVG. OVER REP. 
    TAT_AVG <- df %>%  
      group_by(network, population, true_model, sigma, sample_size) %>% 
      mutate(TAT = 100 * (sum(as.numeric(final_global_model == true_model)) / n()),
        TAT_50 = ifelse(TAT >= 50, 1, 0)) %>%
      summarise(TAT = mean(TAT),
                TAT50 = mean(TAT_50)) 
    
    datalist1[i] <- list(TAT)
    datalist2[i] <- list(TAT_AVG)
  }
    
  TAT <- do.call("rbind", datalist1)
  TAT_AVG <- do.call("rbind", datalist2)
  
  #directory for the files: 
  setwd("D:/data/data_outcome_measures")
  
  #write csv:
  write_csv(TAT, paste0("TAT_TAT50", naming_scheme))
  write_csv(TAT_AVG, paste0("TAT_TAT50_AVG", naming_scheme))

}

#calling the function
TAT50(files)

```

### TAT_C IS NOT REALLY A MEASURE THAT MAKES SENSE WITH A SINGLE GLOBAL MODEL

Data prep for TAT_C_rework.Rmd 

```{r}

#working directory. 
setwd("D:/data/data_prepped_30-11")
path = "D:/data/data_prepped_30-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list 
datalist1 <- list()
datalist2 <- list()

TATC <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
            "colab_cond",
            "network", 
            "population", 
            "sigma",
            "net_size",
            "true_model",
            "prop_1",
            "prop_2",
            "prop_3",
            "prop_4",
            "prop_5",
            "prop_6",
            "prop_7",
            "prop_8",
            "prop_9",
            "prop_10",
            "prop_11",
            "prop_12",
            "prop_13",
            "prop_14",
            "prop_true")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model))
    
    #IF STATEMENT, mutating max prop column..
    if(levels(df$true_model) == "2"){
      
    df$maxprop = names(df[,c(8, 10:22)])[apply(df[,c(8, 10:22)], 
                                                   1, which.max)]
      
    } else if(levels(df$true_model) == "7"){
      
    
    df$maxprop = names(df[,c(8:13, 15:22)])[apply(df[,c(8:13, 15:22)], 
                                                  1, which.max)]
      
    } else if(levels(df$true_model) == "13"){
      
    df$maxprop = names(df[,c(8:19, 21:22)])[apply(df[,c(8:19, 21:22)], 
                                                    1, which.max)]
    
    }
    
    #mutating 1 for TAT_c & 0 for not TAT_c
    df <- df %>%
      mutate(TAT_C = ifelse(maxprop == "prop_true", 1, 0))
    
    #per replica
    TAT_C_REP <- df %>%
      group_by(replica, network, population, sigma, net_size, 
               colab_cond, true_model) %>%
      summarise(TAT_C = round(mean(TAT_C),2)) 
    
    #avg. over rep. 
    TAT_C_AVG <- df %>%
      group_by(network, population, sigma, net_size, colab_cond, true_model) %>%
      summarise(TAT_C = round(mean(TAT_C),2)) 
    
    #putting into lists
    datalist1[i] <- list(TAT_C_REP)
    datalist2[i] <- list(TAT_C_AVG)
    
  }
    
  TAT_C_REP <- do.call("rbind", datalist1)
  TAT_C_AVG <- do.call("rbind", datalist2)
  
  #directory for the files: 
  setwd("E:/data/dataOutcomeMeasures")
  
  #write csv:
  write_csv(TAT_C_REP, "TATC_REP.csv")
  write_csv(TAT_C_AVG, "TATC_AVG.csv")

}

#calling the function
TATC(files)

```

First passage (true accept): 

```{r}

#working directory. 
setwd("D:/data/data_prepped_30-11")
path = "D:/data/data_prepped_30-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list 
datalist1 <- list()

FPTT <- function(files){
  
  #selecting cols (check )
    mycols <- c("turn",
            "studies",
            "replica", 
            "network", 
            "population", 
            "sigma",
            "true_model",
            "prop_t_mod",
            "init_g_true",
            "final_g_true")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          true_model = factor(true_model))
    
    #TAT PER REPLICA
    df <- df %>%
        group_by(replica, population, network, sigma, true_model) %>% 
        summarize(first_row = min(which(final_g_true > init_g_true)))
    
    datalist1[i] <- list(df)
  }
    
  FPTT <- do.call("rbind", datalist1)
  
  #directory for the files: 
  setwd("D:/data/data_outcome_measures")
  
  #write csv:
  write_csv(FPTT, paste0("FPTT", naming_scheme))

}

#calling the function
FPTT(files)

```

