---
title: "Untitled"
author: "Victor Møller"
date: "20 maj 2019"
output: html_document
---

updated 09-11-2019.
Still much work to do. 

```{r}

library(pacman)
p_load(readr, tidyverse, ggplot2, RColorBrewer, reshape2, ggthemes,
       viridis, ggridges, ggunchained, rlang)

```

Preprocessing (should also be adjusted to accommodate better early prep). 

```{r}

#load data 
setwd("E:/data/dataPlotting")

violin <- read_csv("violin_extended.csv")
violinstrat <- read_csv("violin_extended_bystrat.csv")

violin <- violin %>%
mutate(network = factor(network),
      population = factor(population),
      sigma = factor(sigma),
      colab_cond = factor(colab_cond),
      net_size = factor(net_size),
      true_model = factor(true_model),
      strategy = factor("overall"))

violinstrat <- violinstrat %>%
mutate(network = factor(network),
      population = factor(population),
      sigma = factor(sigma),
      colab_cond = factor(colab_cond),
      net_size = factor(net_size),
      true_model = factor(true_model),
      strategy = factor(strategy))

df <- rbind(violin, violinstrat)
```

raincloud prep

```{r}

#preparing raincloud (can be customized)
raincloud_theme = theme(
text = element_text(size = 10),
axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 16),
axis.text = element_text(size = 14),
axis.text.x = element_text(vjust = 0.5),
legend.title=element_text(size=16),
legend.text=element_text(size=16),
legend.position = "right",
plot.title = element_text(lineheight=.8, face="bold", size = 16),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

```

new directory & loading flatViolin

```{r}

setwd("~/CRUST-1")
baseDir <- "."
scriptDir <- paste0(baseDir, "/FunctionsLoads/Functions")
#inputDir <- paste0(baseDir, "/data")
#outputDir <- paste0(baseDir, "/data")
source(paste0(scriptDir, "/flatViolin.R"))


```


Main effects (1). 
Upright plot of main effects avg. over all other grouping variables. 
NO-COLAB COND. 

```{r}

#raincloud plot

RR_FUN <- function(df, .var){
  
  var <- enquo(.var)

g <- df %>%
  filter(strategy == "overall",
         colab_cond == "NOLAB") %>%
  ggplot(aes(x = UQ(var), 
             y = RR, fill = UQ(var))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = RR, color = UQ(var)), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = paste0("Replication rate for ", as_label(var), "s"), #with s?
       subtitle = "Averaged over all other grouping variables",
       x = paste0(as_label(var), "s"), #with s?
       y = "Replication rate") +
  raincloud_theme

#call the plot
g

}

#running the function 
colnames(df)
RR_FUN(df, population)
RR_FUN(df, sigma)
RR_FUN(df, network)
RR_FUN(df, true_model) #looks terrible
RR_FUN(df, net_size) #looks terrible. 

```

Main effects (2). 
Flipped plot of main effects avg. over all other grouping variables. 
NB: same as above (fix this). 

```{r}

#raincloud plot

RR_FUN2 <- function(df, .var){
  
  var <- enquo(.var)

g <- df %>%
  ggplot(aes(x = UQ(var), 
             y = RR, fill = UQ(var))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = RR, color = UQ(var)), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  coord_flip() +
  theme_bw() +
  labs(title = paste0("Replication rate for ", as_label(var), "s"), #with s?
       subtitle = "Averaged over all other grouping variables",
       x = paste0(as_label(var), "s"), #with s?
       y = "Replication rate") +
  raincloud_theme

#call the plot
g

}

#running the function 
colnames(df_RR)
RR_FUN2(df_RR, population)
RR_FUN2(df_RR, sigma)
RR_FUN2(df_RR, network)
RR_FUN2(df_RR, true_model) #looks terrible
RR_FUN2(df_RR, colab_cond) #looks terrible 
RR_FUN2(df_RR, net_size)

```

Interaction effects (1). 
Upright plot of two main effects (possibly interaction)
avg. over all other grouping variables. 
Some of these look terrible bc. we have terrible var names. 
Maybe just hard-code once we have found the plots we want to present. 
Still only NOLAB. 

```{r}

RR_FUN3 <- function(.df, .var1, .var2){
  
  var1 <- enquo(.var1)
  var2 <- enquo(.var2)
  
#raincloud plot
  g <- .df %>%
    filter(strategy == "overall",
         colab_cond == "NOLAB") %>%
    ggplot(aes(x = UQ(var1), y = RR, fill = UQ(var2))) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = RR, color = UQ(var2)), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    #coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var2)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var2))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g

}

#what can we plot over? 
colnames(df)

#population vs. everything: 
RR_FUN3(df, population, network) #tom is lower for all. 
RR_FUN3(df, population, sigma) #some interaction w. BO vs. everyone else. 
RR_FUN3(df, population, true_model) #no real effect. 
RR_FUN3(df, population, net_size) #no effect. 

#network vs. everything 
RR_FUN3(df, network, population) #TOM does worst overall. 
RR_FUN3(df, network, sigma) #TOM does worst overall 
RR_FUN3(df, network, true_model) #TOM does worst overall. 
RR_FUN3(df, network, net_size) #same. 

#sigma vs. everything
RR_FUN3(df, sigma, network) #TOM worst, more spread for 0.2
RR_FUN3(df, sigma, population) #big Tess & Bo effects (unsurprisingly)
RR_FUN3(df, sigma, true_model) #very funky plot (weird interactions). 
RR_FUN3(df, sigma, net_size) #nothing. 

#true model vs. everything 
RR_FUN3(df, true_model, population)  
RR_FUN3(df, true_model, network) #least action/change/diff in TOM
RR_FUN3(df, true_model, sigma) #interaction effect (same as before)
RR_FUN3(df, true_model, net_size) #nothing. 

```

Interaction effects (2). 
Flipped plot of two main effects (possibly interaction)
avg. over all other grouping variables. 

```{r}

RR_FUN4 <- function(.df, .var1, .var2){
  
  var1 <- enquo(.var1)
  var2 <- enquo(.var2)
  
#raincloud plot
  g <- .df %>%
    ggplot(aes(x = UQ(var1), y = RR, fill = UQ(var2))) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = RR, color = UQ(var2)), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var2)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var2))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g

}

#what can we plot over? 
colnames(df_RR)

#population vs. everything: 
RR_FUN4(df_RR, population, network) #tom is lower for all. 
RR_FUN4(df_RR, population, sigma) #some interaction w. BO vs. everyone else. 
RR_FUN4(df_RR, population, true_model) #no real effect. 
RR_FUN4(df_RR, population, colab_cond) #no effect it seems. 

#network vs. everything 
RR_FUN4(df_RR, network, population) #TOM does worst overall. 
RR_FUN4(df_RR, network, sigma) #TOM does worst overall 
RR_FUN4(df_RR, network, true_model) #TOM does worst overall. 
RR_FUN4(df_RR, network, colab_cond) #TOM does worst overall. 

#sigma vs. everything
RR_FUN4(df_RR, sigma, network) #TOM worst, more spread for 0.2
RR_FUN4(df_RR, sigma, population) #big Tess & Bo effects (unsurprisingly)
RR_FUN4(df_RR, sigma, true_model) #interaction effect for sure. 
RR_FUN4(df_RR, sigma, colab_cond) #nothing. 

#true model vs. everything 
RR_FUN4(df_RR, true_model, population)  
RR_FUN4(df_RR, true_model, network) #least action/change/diff in TOM
RR_FUN4(df_RR, true_model, sigma) #interaction effect (same as before)
RR_FUN4(df_RR, true_model, colab_cond) #nothing

#colab condition vs. everything
RR_FUN4(df_RR, colab_cond, network) #nothing
RR_FUN4(df_RR, colab_cond, population) #nothing.
RR_FUN4(df_RR, colab_cond, sigma) #nothing.
RR_FUN4(df_RR, colab_cond, true_model) #nothing. 

```

Potentially create chunk for plots based on true/false replication

------------------

Research strategy: 

```{r}
#raincloud plot

RR_FUN5 <- function(df, .var){
  
  var <- enquo(.var)

g <- df %>%
  filter(colab_cond == "NOLAB") %>%
  ggplot(aes(x = UQ(var), 
             y = RR, fill = UQ(var))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = RR, color = UQ(var)), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = paste0("Replication rate for ", as_label(var), "s"), #with s?
       subtitle = "Averaged over all other grouping variables",
       x = paste0(as_label(var), "s"), #with s?
       y = "Replication rate") +
  raincloud_theme

#call the plot
g

}

#running the function 
colnames(df)
RR_FUN5(df, strategy)

```

```{r}
#raincloud plot

RR_FUN6 <- function(df, .var){
  
  var <- enquo(.var)

g <- df %>%
  filter(strategy == "overall") %>%
  ggplot(aes(x = UQ(var), 
             y = RR, fill = UQ(var))) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = RR, color = UQ(var)), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = paste0("Replication rate for ", as_label(var), "s"), #with s?
       subtitle = "Averaged over all other grouping variables",
       x = paste0(as_label(var), "s"), #with s?
       y = "Replication rate") +
  raincloud_theme

#call the plot
g

}

#running the function 
colnames(df)
RR_FUN6(df, colab_cond)
RR_FUN6(df, sigma)


```

COLAB interactions

```{r}
#raincloud plot

RR_FUN7 <- function(.df, .var1, .var2){
  
  var1 <- enquo(.var1)
  var2 <- enquo(.var2)
  
#raincloud plot
  g <- .df %>%
    ggplot(aes(x = UQ(var1), y = RR, fill = UQ(var2))) +
    geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
    geom_point(aes(y = RR, color = UQ(var2)), 
                    position = position_jitter(width = .15), 
                    size = .5, alpha = 0.8) +
    geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
    expand_limits(x = 2) + #not clear that this changes much. 
    #guides(fill = FALSE) + #legend can be deleted. 
    guides(color = FALSE) +
    scale_fill_tableau() +
    scale_color_tableau() +
    #coord_flip() +
    theme_bw() +
    labs(title = paste0("Replication rate for ", as_label(var1), "s"),
         subtitle = paste0("Grouped by ", as_label(var2)), 
         x = paste0(as_label(var1)), 
         y = "Replication rate",
         fill = paste0(as_label(var2))) + #sets the legend title.
    raincloud_theme
  
  #call the plot
  g

}

#what can we plot over? 
colnames(df)

#population vs. everything: 
RR_FUN7(df, population, colab_cond)
RR_FUN7(df, sigma, colab_cond)
RR_FUN7(df, network, colab_cond)
RR_FUN7(df, true_model, colab_cond)
RR_FUN7(df, colab_cond, strategy)

```


sigma 100 

```{r}

#sigma as factor
small_RR$sigma <- as.factor(small_RR$sigma)

#raincloud plot
g <- small_RR %>%
  filter(sample_size == "100") %>%
  ggplot(aes(x = population, 
                              y = RR, fill = sigma)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
  geom_point(aes(y = RR, color = sigma), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) + #not clear that this changes much. 
  #guides(fill = FALSE) + #legend can be deleted. 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate by population",
       subtitle = "Sample size: 100", 
       x = "Population", 
       y = "Replication rate",
       fill = "Sigma") + #sets the legend title.
  raincloud_theme

#call the plot
g

```

for sample size 20

```{r}

#raincloud plot
g1 <- small_RR %>%
  filter(sample_size == "20") %>%
  ggplot(aes(x = population, 
                              y = RR, fill = sigma)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
  geom_point(aes(y = RR, color = sigma), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) + #not clear that this changes much. 
  #guides(fill = FALSE) + #legend can be deleted. 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate by population",
       subtitle = "Sample size: 20", 
       x = "Population", 
       y = "Replication rate",
       fill = "Sigma") + #sets the legend title.
  raincloud_theme

#call the plot
g1

library(cowplot)
plot_grid(g, g1)

```

