---
title: "qualitative"
author: "Mikkel Werling & Victor Moeller"
date: "5/16/2019"
output: html_document
---

Updated on 31-10-2019.
Now up to the changes made in the rework-session. New constants, fewer variables. This is the document for the TOM-networks and 484-sized networks in general. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

packages

```{r}
library(pacman)

p_load(igraph, stringr, ggraph, wesanderson, cowplot, caTools, data.table, permute, matrixStats, MCMCpack, tidyverse, rlist)

```

paths

```{r}
baseDir <- "~/CRUST-1" #the "." stopped working. 
scriptDir <- paste0(baseDir, "/src/functions")
inputDir <- paste0(baseDir, "/data")
outputDir <- paste0(baseDir, "/data/new_data")
```

functions

```{r}
source(paste0(scriptDir, "/analysis.R"))
source(paste0(scriptDir, "/calculateDet.R"))
source(paste0(scriptDir, "/calculateDistance.R"))
source(paste0(scriptDir, "/compareModels.R"))
source(paste0(scriptDir, "/constants_4_rework.R")) #new constants baby.
source(paste0(scriptDir, "/convertBinary.R"))
source(paste0(scriptDir, "/generateBetas.R"))
source(paste0(scriptDir, "/generateModels.R"))
source(paste0(scriptDir, "/generateXSet.R"))
source(paste0(scriptDir, "/generateY.R"))
source(paste0(scriptDir, "/getBetas.R"))
source(paste0(scriptDir, "/getPredictors.R"))
source(paste0(scriptDir, "/modelSimilarByInteraction.R"))
source(paste0(scriptDir, "/modelSimilarByTerm.R"))
source(paste0(scriptDir, "/modelToStr.R"))
source(paste0(scriptDir, "/searchModel.R"))
source(paste0(scriptDir, "/seedGenerator.R"))
source(paste0(scriptDir, "/simulator.R"))
source(paste0(scriptDir, "/strToModel.R"))
source(paste0(scriptDir, "/ABM_TOM_rework.R")) #TOM cit. network. 
```

some_models, g & agentTurn

```{r}

#some models -  
load(paste0(baseDir, "/connectivity/loads/some_models"))

```

input parameters

```{r}

## Number of replications
replications <- 2 #100 originally, now 2. 

## Length of the simulation
turns <- 2000

## Number of factors
k <- 3

## generating 
load(paste0(baseDir, "/connectivity/loads/models")) #changed

## Identify the number of predictors of each model
predictors <- getPredictors(models)

## Generate Betas
weights <- generateBetas(models)

## Correlation
correlation <- 0.2

## modelCompare & selection
modelSelection <- "hard"

## ndec
ndec = 4

## outputs
outputFile <- ".csv" 
paramFile <- ".rds"

## verbose
verbose <- TRUE
```

For output. 
These are the parameters we don't vary. 

```{r}
net_size <- 484

```

setting seeds

```{r}
seeds <- seedGenerator(replications, paste0(inputDir, "/seeds.csv"))

```

FULL RUN: 
defining parameters

```{r}
net_types <- list("Lattice", "Small", "TOM")
sigmas <- list(0.2, 0.5, 0.8) #0.2 & 0.8 deleted. 
base_sampleSizes <- list(20, 100) #20 deleted. 
pop_types <- list("Bo", "Tess", "Mave", "All")
tMods <- list(2, 7, 13)
modelCompares <- list(BIC, AIC)
colab_probs <- list(0, 0.02) #no colab vs. colab. 

```

running the ABM. 

```{r}

start_time <- Sys.time()

### running the ABM for all combinations of parameters ### 

for(net_type in net_types){ 
  for(sigma in sigmas){
    for(base_sampleSize in base_sampleSizes){
      for(pop_type in pop_types){
        for(tMod in tMods){ #not sure this works. 
          for(modelCompare in modelCompares){
            for(colab_prob in colab_probs){
        
ABM_TOM(replications, turns, models, k, 
    weights, base_sampleSize, correlation, sigma,
    modelCompare, modelSelection, inputDir, outputDir, outputFile, paramFile,
    verbose, ndec, seeds, some_models)
            }
          }
        }
      }
    }
  }
}

end_time <- Sys.time()
end_time - start_time

```

SPECIFIC PARAMETERS:
Just change the hell out of this so that it suits your needs. 

```{r}
net_types <- list("TOM") #"Lattice", "Small", "TOM"
sigmas <- list(0.5) #0.2, 0.5, 0.8 
base_sampleSizes <- list(100) #20, 100. 
pop_types <- list("Tess") #"Bo", "Mave", "Tess", "All"
tMods <- list(13) #2, 7, 13. 
modelCompares <- list(BIC) #AIC, BIC 
colab_probs <- list(0, 0.02) #no colab vs. colab. 
```

```{r}

start_time <- Sys.time()

### running the ABM for all combinations of parameters ### 

for(net_type in net_types){ 
  for(sigma in sigmas){
    for(base_sampleSize in base_sampleSizes){
      for(pop_type in pop_types){
        for(tMod in tMods){ #not sure this works. 
          for(modelCompare in modelCompares){ #should be
            for(colab_prob in colab_probs){
        
ABM_TOM(replications, turns, models, k, 
    weights, base_sampleSize, correlation, sigma,
    modelCompare, modelSelection, inputDir, outputDir, outputFile, paramFile,
    verbose, ndec, seeds, some_models)
            }
          }
        }
      }
    }
  }
}

end_time <- Sys.time()
end_time - start_time

```

