---
title: "prep_BA_reworkLOOP"
author: "Victor Møller"
date: "November 14, 2019"
output: html_document
---
14-09-2019
This document tests & cleans data from ABM5. 
It is probably only going to work for test-phase with small
amounts of data. It takes data from "new_data" folder and outputs to "tests".

```{r}

#packages
library(pacman)
p_load(tidyverse, tidyselect, data.table)

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

```

do we have all files.

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#Working directory of RAW data. 
setwd("E:/data/27-11")

#which files do we have
files = list.files(pattern=c("*.csv"), full.names=TRUE)

#do we lack anything 

#networks
identifiers <- c("Small", "Lattice", "TOM", "PT", 
              "_Mave_", "_Tess_", "_All_", "_Bo_",
              "_0.2_", "_0.5_", "_0.8_", 
              "_413_", "_484_",
              "_2_", "_7_", "_13_",
              "_COLAB", "_NOLAB")

for (i in identifiers){
  
network <- noquote(i)

#quick check: 
x <- files
network <- str_detect(files, i)
subset <- x[network]
value <- length(unlist(subset))
print(paste0(value, ": ", i))

}


```


First chunk is a screening of the data. 
Does it pass our sanity checks & do we have all cases? 

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#Working directory of RAW data. 
setwd("D:/data_new1")

#for basic tests
condition <- list()
network <- list()
population <- list()
sigma <- list()
true_model <- list()
replica <- list()

#for other tests 
studiesMAX <- list()
studiesMIN <- list()

#the masterlist
masterlist <- list()

#your files 
files = list.files(pattern=c("*.csv"), full.names=TRUE)

#running the function
datacheck <- function(i){
  
  for(i in files){
    
  #reading data
  data <- read_csv(i)
  data <- na.omit(data)
  data <- tibble::as_tibble(data)
  
  #factorizing 
  data <- data %>%
  mutate(network = factor(network),
         population = factor(population),
         sigma = factor(sigma),
         net_size = factor(net_size),
         true_model = factor(true_model),
         colab_cond = factor(colab_cond),
         orig_type = factor(orig_type),
         strategy = factor(strategy))
  
  #basic tests 
  condition[i] <- paste0(i)
  network[i] <- levels(data$network)
  population[i] <- levels(data$population)
  sigma[i] <- levels(data$sigma)
  true_model[i] <- levels(data$true_model)
  replica[i] <- sum(unique(data$replica))
  
  #more tests 1: all replicas 10,000. 
  check <- data %>%
  group_by(replica, network, population, sigma, true_model,
          net_size, colab_cond) %>%
  summarize(stud = max(studies))
  
  studiesMAX[i] <- min(check$stud) #10,000
  studiesMIN[i] <- max(check$stud) #10,000
  
  }
  
  masterlist <- list(network, population, sigma,
                     true_model, replica, studiesMAX, studiesMIN)
  return(masterlist)
  
}

test <- datacheck(files)

## taking out parameters 
network <- unname(unlist(test[[1]]))
population <- unname(unlist(test[[2]]))
sigma <- unname(unlist(test[[3]]))
true_model <- unname(unlist(test[[4]]))
replica <- unname(unlist(test[[5]]))
studiesMAX <- unname(unlist(test[[6]]))
studiesMIN <- unname(unlist(test[[7]]))

#checking
network
population
sigma
true_model
replica
studiesMAX
studiesMIN

```

write the cleaned files into another directory

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#Working directory of RAW data. 
setwd("D:/data_new1")

#your files 
files = list.files(pattern=c("*.csv"), full.names=TRUE)

#the function
datawrite <- function(i){
  
  for(i in files){
  
  #where your raw files are:   
  setwd("D:/data_new1")
    
  #reading data:
  data <- read_csv(i)
  data <- na.omit(data)
  data <- tibble::as_tibble(data)
  
  #factorizing (might not work anyways): 
  data <- data %>%
  mutate(network = factor(network),
         population = factor(population),
         sigma = factor(sigma),
         net_size = factor(net_size),
         true_model = factor(true_model),
         colab_cond = factor(colab_cond),
         orig_type = factor(orig_type),
         strategy = factor(strategy))
  
  #directory for the files: 
  setwd("D:/data_prepped1")
  
  #write csv:
  write_csv(data, paste0(i))
  
  }
}

datawrite(files)


```

Data preparation for model sampling: 

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#working directory
setwd("E:/data/data_prepped_27-11")
path = "E:/data/data_prepped_27-11"
files <- list.files(path = path, pattern = "*.csv")

#initializing empty list 
datalist1 <- list()
datalist2 <- list()

samplingFX <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
            "strategy",
            "orig_type", #needed directly
            "old_model", #needed directly
            "selected_model") #needed directly 
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(strategy = factor(strategy),
          orig_type = factor(orig_type),
          old_model = factor(old_model),
          selected_model = factor(selected_model))
    
    #any sampling of own models? 
    df_errors <- df %>%
        filter(strategy != "colab") %>%
        group_by(orig_type) %>%
        summarize(count = sum(old_model == selected_model))
    
    #sampling distributions 
    df_sampling <- df %>%
        filter(strategy == "research") %>%
        group_by(orig_type, old_model, selected_model) %>%
        summarize(count = n())
    
    datalist1[i] <- list(df_errors)
    datalist2[i] <- list(df_sampling)
  }
    
  df_errors <- do.call("rbind", datalist1)
  df_sampling <- do.call("rbind", datalist2)
  
  #directory for the files: 
  setwd("E:/data/dataSampling")
  
  #write csv:
  write_csv(df_errors, paste0("df_errors", naming_scheme))
  write_csv(df_sampling, paste0("df_sampling", naming_scheme))

}

#calling the function
samplingFX(files)

```

data preparation for "violin_extended_rework": 
Consider including the column with final_global_true_model 
so that we can group based on whether they sampled the true model. 

```{r}
#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#working directory. 
setwd("E:/data/data_prepped_27-11")
path = "E:/data/data_prepped_27-11"
files <- list.files(path = path, pattern="*.csv")


#initializing empty list 
datalist1 <- list()
datalist2 <- list()

violin_extended_rework <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
            "turn", 
            "studies", 
            "network", 
            "population", 
            "sigma",
            "colab_cond",
            "net_size",
            "true_model",
            "strategy",
            "switch_rep_study",
            "switch_rep",
            "prop_true",
            "prop_t_mod")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model),
          strategy = factor(strategy))
    
    #create DF. 
    df_basic <- df %>%
        group_by(replica, network, population, sigma, true_model,
          net_size, colab_cond) %>%
        summarize(RR = sum(switch_rep) / 
              sum(switch_rep_study)) 
    
    #grouping by strategy 
    df_strat <- df %>%
        group_by(replica, network, population, sigma, true_model,
          net_size, colab_cond, strategy) %>%
        summarize(RR = sum(switch_rep) / 
              sum(switch_rep_study))
    
    datalist1[i] <- list(df_basic)
    datalist2[i] <- list(df_strat)
  }
    
  df <- do.call("rbind", datalist1)
  df_strat <- do.call("rbind", datalist2)
  
  #directory for the files: 
  setwd("E:/data/dataPlotting")
  
  #write csv:
  write_csv(df, "violin_extended.csv")
  write_csv(df_strat, "violin_extended_bystrat.csv")

}

#calling the function
violin_extended_rework(files)

```

data preparation for "violin_ridges_rework":

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#working directory.
setwd("E:/data/data_prepped_27-11")
path = "E:/data/data_prepped_27-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list
datalist1 <- list()
datalist2 <- list()
datalist3 <- list()

violin_ridges_rework <- function(files){
 
  #selecting cols (check )
    mycols <- c("replica", 
            "turn", #need this??
            "studies", 
            "network", 
            "colab_cond",
            "population", 
            "sigma",
            "net_size",
            "true_model",
            "strategy",
            "switch_rep_study",
            "switch_rep",
            "prop_true",
            "prop_t_mod") #importantly. 
 
  for(i in files){

    #read csv
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model),
          strategy = factor(strategy))
    
    #replication rate & TAT overall
    RR_TAT <- df %>%
    group_by(replica, network, population, sigma, true_model,
            net_size, colab_cond) %>%
    summarize(RR = sum(switch_rep) / sum(switch_rep_study),
              TAT = mean(prop_true)) 

    #replication rate & TAT (for )
    #legit to compute TAT for the subset?
    RR_TAT_TF <- df %>%
    group_by(prop_t_mod, replica, network, population, sigma, true_model, 
             net_size, colab_cond) %>%
    summarize(RR = sum(switch_rep) / sum(switch_rep_study),
              TAT = mean(prop_true))
    
    #grouped by strategy:
    RR_TAT_BYSTRAT <- df %>%
    group_by(replica, prop_t_mod, network, 
             population, sigma, true_model, 
             net_size, colab_cond, strategy) %>%
    summarize(RR = sum(switch_rep) / sum(switch_rep_study),
              TAT = mean(prop_true))
    
    datalist1[i] <- list(RR_TAT)
    datalist2[i] <- list(RR_TAT_TF)
    datalist3[i] <- list(RR_TAT_BYSTRAT)
  }
    
  RR_TAT <- do.call("rbind", datalist1)
  RR_TAT_TF <- do.call("rbind", datalist2)
  RR_TAT_BYSTRAT <- do.call("rbind", datalist3)
 
  #directory for the files:
  setwd("E:/data/dataPlotting")
 
  #write csv:
  write_csv(RR_TAT, "violin_ridges_RR.csv")
  write_csv(RR_TAT_TF, "violin_ridges_TF.csv")
  write_csv(RR_TAT_BYSTRAT, "violin_ridges_BYSTRAT.csv")

}

#calling the function
violin_ridges_rework(files)

```

true_false plot - only true:

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#working directory. 
setwd("E:/data/data_prepped_27-11")
path = "E:/data/data_prepped_27-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list 
datalist <- list()

true_false_rework <- function(files){
  
  #selecting cols (check )
    mycols <- c("population", 
            "sigma",
            "true_model",
            "studies",
            "network",
            "net_size",
            "replica",
            "colab_cond",
            "prop_true")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model))
    
    #downsampling
    df <- df[seq(1, nrow(df), 50), ]
    
    
    #melting the variables
    naming <- colnames(df)
    
    #data
    df <- df %>%
    melt(id = c(naming[1:8])) %>% 
    mutate(true = ifelse(variable == "prop_true", "True", "False")) %>% 
    mutate(variable = relevel(variable, ref = "prop_true")) %>% 
    mutate(variable = fct_rev(variable)) 
    
    datalist[i] <- list(df)
  }
    
  df_final <- do.call("rbind", datalist)
  
  #directory for the files: 
  setwd("E:/data/dataPlotting")
  
  #write csv:
  write_csv(df_final, paste0("TF_rework_only_true", 
                             naming_scheme))
}



#calling the function
true_false_rework(files)
```

true_false with false 

NOTE: Implementing a paste0 approach. Splits up the different networks and writes the files. 

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#working directory. 
setwd("E:/data/data_prepped_27-11")
path = "E:/data/data_prepped_27-11"
#files <- list.files(path = path, pattern="^PT.*.csv") #USING REGEX TO INDICATE THE SUBSET

#initializing empty list 
datalist <- list()

true_false_CON <- function(files, identifier){
  
  #selecting cols (check )
    mycols <- c("population", 
            "sigma",
            "true_model",
            "studies",
            "network",
            "net_size",
            "replica",
            "colab_cond",
            "prop_1",
            "prop_2",
            "prop_3",
            "prop_4",
            "prop_5",
            "prop_6",
            "prop_7",
            "prop_8",
            "prop_9",
            "prop_10",
            "prop_11",
            "prop_12",
            "prop_13",
            "prop_14",
            "prop_true")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model))
    
    #downsampling
    df <- df[seq(1, nrow(df), 50), ]
    
    
    #melting the variables
    naming <- colnames(df)
    df <- df %>%
    melt(id = c(naming[1:8])) %>% #melting with proportions becoming variable and their values becoming values
    mutate(true = ifelse(variable == "prop_true", "True", "False")) %>% #making a identifying column in order to color                                                                           for the plot
    mutate(variable = relevel(variable, ref = "prop_true")) %>% #releveling so that proportion true is considered first
    mutate(variable = fct_rev(variable)) #releveling so that proportion true is considered last - this is done in order                                           to make it the top layer in the overlay between different smooths.
    
    datalist[i] <- list(df)
  }
    
  df_final <- do.call("rbind", datalist)
  
  #directory for the files: 
  setwd("E:/data/dataPlotting")
  
  #write csv:
  write_csv(df_final, paste0(identifier, "_true_false_CON.csv"))

}

#WHAT NETWORKS ARE YOU SUBSETTING:
subset_variables <- c("Lattice", "Small", "PT") #or TOM

for (i in subset_variables){
  files <- list.files(path = path, pattern=paste0("^", i, ".*.csv"))
  
  true_false_CON(files, i)
}


```


###OUTCOME MEASURES:
____________________
Data prep for "Stickiness":

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#working directory. 
setwd("E:/data/data_prepped_27-11")
path = "E:/data/data_prepped_27-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list 
datalist <- list()

stickiness_rework <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
                "network", 
                "population", 
                "sigma",
                "true_model",
                "net_size", #maybe relevant.
                "colab_cond",
                "prop_t_mod", #proposed true? (1 = yes, 0 = no). 
                "init_g_true", #count of true orig. (testing) agents.
                "final_g_true", #count of post stud. (testing) agents. 
                "switch_true",
                "switch_true_changing")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model))
    
    #create DF
    df <- df %>%
      filter(prop_t_mod == 0) %>%
      group_by(replica, sigma, population, network, true_model,
           net_size, colab_cond) %>%
      summarize(agent_away = sum(as.numeric(init_g_true == 1 & 
                                        final_g_true == 0)),
            agent_total = sum(as.numeric(init_g_true == 1)),
            switch_away = sum(switch_true_changing),
            switch_total = sum(switch_true))
    
    datalist[i] <- list(df)
  }
    
  df_final <- do.call("rbind", datalist)
  
  #directory for the files: 
  setwd("E:/data/dataOutcomeMeasures")
  
  #write csv:
  write_csv(df_final, "stickiness_rework.csv")

}

#calling the function
stickiness_rework(files)
```

Data prep for TAT_TAT50_rework.Rmd 

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#working directory. 
setwd("E:/data/data_prepped_27-11")
path = "E:/data/data_prepped_27-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list 
datalist1 <- list()
datalist2 <- list()

TAT50 <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
                "network", 
                "population", 
                "sigma",
                "net_size",
                "colab_cond",
                "true_model",
                "base_SS",
                "prop_true")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model))
    
    #TAT PER REPLICA
    TAT <- df %>%  
      mutate(TAT_50 = ifelse(prop_true >= 0.5, 1, 0)) %>%
      group_by(replica, network, population, true_model, sigma, net_size, 
               base_SS, colab_cond) %>% 
      summarise(TAT = mean(prop_true),
                TAT50 = mean(TAT_50)) 
        
    #TAT AVG. OVER REP. 
    TAT_AVG <- df %>%  
      mutate(TAT_50 = ifelse(prop_true >= 0.5, 1, 0)) %>%
      group_by(network, population, true_model, sigma, net_size, 
               base_SS, colab_cond) %>% 
      summarise(TAT = mean(prop_true),
                TAT50 = mean(TAT_50)) 
    
    datalist1[i] <- list(TAT)
    datalist2[i] <- list(TAT_AVG)
  }
    
  TAT <- do.call("rbind", datalist1)
  TAT_AVG <- do.call("rbind", datalist2)
  
  #directory for the files: 
  setwd("E:/data/dataOutcomeMeasures")
  
  #write csv:
  write_csv(TAT, "TAT_TAT50.csv")
  write_csv(TAT_AVG, "TAT_TAT50_AVG.csv")

}

#calling the function
TAT50(files)

```

Data prep for TAT_C_rework.Rmd

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#working directory. 
setwd("E:/data/data_prepped_27-11")
path = "E:/data/data_prepped_27-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list 
datalist1 <- list()
datalist2 <- list()

TATC <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
            "colab_cond",
            "network", 
            "population", 
            "sigma",
            "net_size",
            "true_model",
            "prop_1",
            "prop_2",
            "prop_3",
            "prop_4",
            "prop_5",
            "prop_6",
            "prop_7",
            "prop_8",
            "prop_9",
            "prop_10",
            "prop_11",
            "prop_12",
            "prop_13",
            "prop_14",
            "prop_true")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model))
    
    #IF STATEMENT, mutating max prop column..
    if(levels(df$true_model) == "2"){
      
    df$maxprop = names(df[,c(8, 10:22)])[apply(df[,c(8, 10:22)], 
                                                   1, which.max)]
      
    } else if(levels(df$true_model) == "7"){
      
    
    df$maxprop = names(df[,c(8:13, 15:22)])[apply(df[,c(8:13, 15:22)], 
                                                  1, which.max)]
      
    } else if(levels(df$true_model) == "13"){
      
    df$maxprop = names(df[,c(8:19, 21:22)])[apply(df[,c(8:19, 21:22)], 
                                                    1, which.max)]
    
    }
    
    #mutating 1 for TAT_c & 0 for not TAT_c
    df <- df %>%
      mutate(TAT_C = ifelse(maxprop == "prop_true", 1, 0))
    
    #per replica
    TAT_C_REP <- df %>%
      group_by(replica, network, population, sigma, net_size, 
               colab_cond, true_model) %>%
      summarise(TAT_C = round(mean(TAT_C),2)) 
    
    #avg. over rep. 
    TAT_C_AVG <- df %>%
      group_by(network, population, sigma, net_size, colab_cond, true_model) %>%
      summarise(TAT_C = round(mean(TAT_C),2)) 
    
    #putting into lists
    datalist1[i] <- list(TAT_C_REP)
    datalist2[i] <- list(TAT_C_AVG)
    
  }
    
  TAT_C_REP <- do.call("rbind", datalist1)
  TAT_C_AVG <- do.call("rbind", datalist2)
  
  #directory for the files: 
  setwd("E:/data/dataOutcomeMeasures")
  
  #write csv:
  write_csv(TAT_C_REP, "TATC_REP.csv")
  write_csv(TAT_C_AVG, "TATC_AVG.csv")

}

#calling the function
TATC(files)

```

First passage (true accept): 

```{r}

#Naming scheme:
naming_scheme <- "_MetascienceBA.csv"

#working directory. 
setwd("E:/data/data_prepped_27-11")
path = "E:/data/data_prepped_27-11"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list 
datalist1 <- list()

FPTT <- function(files){
  
  #selecting cols (check )
    mycols <- c("turn",
            "studies",
            "replica", 
            "network", 
            "population", 
            "sigma",
            "true_model",
            "net_size",
            "colab_cond",
            "prop_t_mod",
            "init_g_true",
            "final_g_true",
            "orig_agents",
            "switch_testing")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model))
    
    #TAT PER REPLICA
    df <- df %>%
        group_by(replica, population, network, sigma, true_model, net_size, 
           colab_cond) %>% 
        summarize(first_row = min(which(final_g_true > init_g_true)),
            first_study = studies[first_row],
            orig_agents = orig_agents[first_row],
            switch_testing = switch_testing[first_row])
    
    datalist1[i] <- list(df)
  }
    
  FPTT <- do.call("rbind", datalist1)
  
  #directory for the files: 
  setwd("E:/data/dataOutcomeMeasures")
  
  #write csv:
  write_csv(FPTT, "FPTT.csv")

}

#calling the function
FPTT(files)

```

