---
title: "replication scaled"
author: "Victor Møller"
date: "19 maj 2019"
output: html_document
---

```{r}
#set working directory
setwd("~/CRUST-1/data/tests")

#packages 
library(pacman)
p_load(tidyverse, ggunchained) 
```

loading data. 

```{r}

#reading 
path <- "~/CRUST-1/data/tests/"

files <- list.files(path = path, pattern="*.csv") #if possible. 

mycols <- c("replica", 
            "network", 
            "population", 
            "sigma",
            "net_size",
            "base_SS",
            "true_model",
            "colab_cond",
            "switch_rep_study",
            "switch_rep",
            "init_g_true",
            "final_g_true",
            "prop_t_mod")

#loading them 
dfList <- lapply(files, function(f) {  
   read.csv(paste0(path, f))[mycols]
})

#subsetting (because of computational demands)
df <- do.call(rbind, dfList) 
rm(dfList)
```

How many total variations (for overview)

```{r}

var <- df %>%
  group_by(network, population, sigma, net_size, colab_cond,
           base_SS, true_model) %>%
  summarize(n())

rm(var)

```

replication overall (used for overview)

```{r}
#replication overall 
df_overall <- df %>%
  group_by(replica, network, population, sigma, net_size, colab_cond, 
           base_SS, true_model) %>%
  summarize(replicated = sum(switch_rep) / sum(switch_rep_study),
            number = sum(switch_rep_study)) %>%
  ungroup()
```

Next chunk: 
Checking max & min number of replication studies.
Which conditions, do we have enough & is it interesting?

```{r}

#checking for low number of rep. studies
low <- df_overall[order(df_overall$number),]
low <- low[,-c(1)]
low

high <- df_overall[order(-df_overall$number),]
high <- high[,-c(1)]
high

rm("high", "low")

```

Comments for above chunk: 
So far it seems that we have most replications in "bad" conditions 
with low replication rate and fewest replications in "good" conditions
with high replication rate. It seems that high replication rate 
(as it should) is affected by sigma (I.e., with higher certainty there is 
higher replication rate). 

Next chunk:
Grouping by TRUE prop. mod. 
How many rep. studies in diff. conditions?

```{r}
#making the global dataframe.
df_byglobal <- df %>%
  group_by(prop_t_mod, replica, network, population, sigma, net_size, colab_cond, 
           base_SS, true_model) %>%
  summarize(replicated = sum(switch_rep) / sum(switch_rep_study),
            number = sum(switch_rep_study)) %>%
  ungroup()

#finding min. amount of rep. studies. 
low <- df_byglobal[order(df_byglobal$number),]
low <- low[,-c(2,10)]
low

#making dataframe not grouped by replica
df_byglobal1 <- df %>%
  group_by(prop_t_mod, network, population, sigma, net_size, colab_cond, 
           base_SS, true_model) %>%
  summarize(replicated = sum(switch_rep) / sum(switch_rep_study),
            number = sum(switch_rep_study)) %>%
  ungroup()

#finding min. amount of rep. studies. 
low <- df_byglobal1[order(df_byglobal1$number),]
low <- low[,-c(9)]
low

rm(low)
```

Above chunk: 
Some replicas without any replication studies of TRUE model (especially sig. 0.8)
Still some with very few when combining 5 reps. 
Should be OK though. 

Next chunk: 
overall summary stats (not grouped by true/not true).

```{r}
#summary stats
df_overall_sum <- df_overall %>%
  group_by(network, population, sigma, net_size, colab_cond, 
           base_SS, true_model) %>%
  summarize(RR_median = median(replicated),
            RR_mean = mean(replicated),
            RR_IQR = IQR(replicated),
            RR_SD = sd(replicated)) %>%
  ungroup()

#lowest replication rates.  
low_rep <- df_overall_sum[order(df_overall_sum$RR_mean),]
head(low_rep)

#highest replication rates.
high_rep <- df_overall_sum[order(-df_overall_sum$RR_mean),]
head(high_rep)

rm("low_rep", "high_rep")

```

Comments on above chunk: 
all lowest replication rates are in the TOM condition (worrying?)
Generally rep. rate is lower than 50%. 
TESS seems to be the best replicator & MAVE the worst. 

Next chunk:
Testing differences in replication rates for TRUE/FALSE
focusing on different grouping variables. 
This section ignores interactions & only focuses on main effects. 

```{r}
#replication based on TRUE/FALSE & NETWORKS
byglobal_network <- df_byglobal %>%
  group_by(prop_t_mod, network) %>%
  summarize(RR_median = median(replicated, na.rm = TRUE),
            RR_mean = mean(replicated, na.rm = TRUE),
            RR_IQR = IQR(replicated, na.rm = TRUE),
            RR_SD = sd(replicated, na.rm = TRUE)) %>%
  ungroup()

byglobal_network

#replication based on TRUE/FALSE & POPULATIONS
byglobal_pop <- df_byglobal %>%
  group_by(prop_t_mod, population) %>%
  summarize(RR_median = median(replicated, na.rm = TRUE),
            RR_mean = mean(replicated, na.rm = TRUE),
            RR_IQR = IQR(replicated, na.rm = TRUE),
            RR_SD = sd(replicated, na.rm = TRUE)) %>%
  ungroup()

byglobal_pop

#replication based on TRUE/FALSE & SIGMA
byglobal_sigma <- df_byglobal %>%
  group_by(prop_t_mod, sigma) %>%
  summarize(RR_median = median(replicated, na.rm = TRUE),
            RR_mean = mean(replicated, na.rm = TRUE),
            RR_IQR = IQR(replicated, na.rm = TRUE),
            RR_SD = sd(replicated, na.rm = TRUE)) %>%
  ungroup()

byglobal_sigma

#replication based on TRUE/FALSE & T_MOD
byglobal_tmod <- df_byglobal %>%
  group_by(prop_t_mod, true_model) %>%
  summarize(RR_median = median(replicated, na.rm = TRUE),
            RR_mean = mean(replicated, na.rm = TRUE),
            RR_IQR = IQR(replicated, na.rm = TRUE),
            RR_SD = sd(replicated, na.rm = TRUE)) %>%
  ungroup()

byglobal_tmod

#replication based on TRUE/FALSE & COLAB
byglobal_colab <- df_byglobal %>%
  group_by(prop_t_mod, colab_cond) %>%
  summarize(RR_median = median(replicated, na.rm = TRUE),
            RR_mean = mean(replicated, na.rm = TRUE),
            RR_IQR = IQR(replicated, na.rm = TRUE),
            RR_SD = sd(replicated, na.rm = TRUE)) %>%
  ungroup()

byglobal_colab

#replication based on TRUE/FALSE & base_SS
byglobal_SS <- df_byglobal %>%
  group_by(prop_t_mod, base_SS) %>%
  summarize(RR_median = median(replicated, na.rm = TRUE),
            RR_mean = mean(replicated, na.rm = TRUE),
            RR_IQR = IQR(replicated, na.rm = TRUE),
            RR_SD = sd(replicated, na.rm = TRUE)) %>%
  ungroup()

byglobal_SS

```

Above chunk: 
(1) byglobal_network: consistently higher RR for TRUE (~50%) than false (~30%).
TOM generally has somewhat lower rep. rate (mean, median) than SMALL/LAT. 
However, This also means that he is as good at distinguishing..
SMALL has quite a high RR median & TOM has quite a low RR median (for TRUE). 

(2) byglobal_pop: consistently higher RR for true (~35-50%) than false (~30%).
Bo has very high rep. rate of true model (Mave also doing good). 
Tess replicates the most false models. 

(3) byglobal_sigma: Crazy high RR for TRUE/0.2 (80%).
However, the RR for TRUE/0.8 (20%) is lower than both FALSE. 
Also, there seems to be an interaction effect here. 

(4) byglobal_colab: Does not seem to affect rates. 
Both FALSE conditions (~30%) and both TRUE conditions (~50%).

(5) byglobal_tmod: consistently higher RR for TRUE (~40-50%) than FALSE (~30%).
However, the difference is bigger for mod2 than mod13 suggesting that they
are better at selecting here. 

Next chunk:
Investigating TRUE replications only 

```{r}

#sum over some parameters. 
df_byglobal_sum <- df_byglobal %>%
  group_by(prop_t_mod, network, population, net_size) %>%
  summarize(RR_true_median = median(replicated, na.rm = TRUE),
            RR_true_mean = mean(replicated, na.rm = TRUE),
            RR_true_IQR = IQR(replicated, na.rm = TRUE),
            RR_true_SD = sd(replicated, na.rm = TRUE)) %>%
  ungroup()

#only true 
df_true_sum <- df_byglobal_sum %>%
  filter(prop_t_mod == 1) %>%
  dplyr::select(network, population, RR_true_median, RR_true_IQR, 
         RR_true_mean, RR_true_SD)

```



write.csv

```{r}
#working directory 
setwd("~/CRUST-1/connectivity/outcome_results/sample_size_20")

#writing csv. 
write.csv(df_overall_sum, "RR_small_20.csv", row.names = F)
write.csv(df_true_sum, "RRT_small_20.csv", row.names = F)

#testing 
read.csv("RR_small_20.csv")
read.csv("RRT_small_20.csv")

#testing 
head(RR_lattice_100)
head(RR_small_100)
head(RRT_lattice_100)
head(RRT_small_100)

```
