---
title: "stickiness"
author: "Mikkel Werling"
date: "5/19/2019"
output: html_document
---


```{r}

#set working directory
setwd("~/CRUST-1/data/tests")

#packages 
library(pacman)
p_load(tidyverse, ggunchained) 
```

loading data. 

```{r}
#reading 
path <- "~/CRUST-1/data/tests/"

files <- list.files(path = path, pattern="*.csv") #if possible. 

mycols <- c("replica", 
            "network", 
            "population", 
            "sigma",
            "true_model",
            "net_size", #maybe relevant.
            "colab_cond",
            "base_SS", #maybe relevant. 
            "prop_t_mod", #proposed true? (1 = yes, 0 = no). 
            "init_g_true", #count of true orig. (testing) agents.
            "final_g_true", #count of post stud. (testing) agents. 
            "switch_true",
            "switch_true_changing")

#loading them 
dfList <- lapply(files, function(f) {  
   read.csv(paste0(path, f))[mycols]
})

#subsetting (because of computational demands)
df <- do.call(rbind, dfList) 
rm(dfList)

```

Next chunk:
Making the dataframe that we compute everything else based on: 

```{r}

#prep data frame.  
df1 <- df %>%
  filter(prop_t_mod == 0) %>%
  group_by(replica, sigma, population, network, true_model,
           net_size, colab_cond, base_SS) %>%
  summarize(agent_away = sum(as.numeric(init_g_true == 1 & 
                                        final_g_true == 0)),
            agent_total = sum(as.numeric(init_g_true == 1)),
            switch_away = sum(switch_true_changing),
            switch_total = sum(switch_true))

```

next chunk: 
stickiness based on agents vs. switch vs. combined. 
avg. over network & population. 

```{r}
#only orig. agents 
df_agents <- df1 %>%
  mutate(stickiness = 1 - (agent_away / agent_total)) %>%
  group_by(network, population) %>%
  summarize(stickiness_median = median(stickiness),
            stickiness_mean = mean(stickiness),
            stickiness_IQR = IQR(stickiness), 
            stickiness_SD = sd(stickiness))

#only switch. agents
df_switch <- df1 %>%
  mutate(stickiness = 1 - (switch_away / switch_total)) %>%
  group_by(network, population) %>%
  summarize(stickiness_median = median(stickiness),
            stickiness_mean = mean(stickiness),
            stickiness_IQR = IQR(stickiness), 
            stickiness_SD = sd(stickiness))

#combined stickiness
df_combined <- df1 %>%
  mutate(lose_global = agent_away + switch_away,
         all_global = agent_total + switch_total,
         stickiness = 1 - (lose_global / all_global)) %>%
  group_by(network, population) %>%
  summarize(stickiness_median = median(stickiness),
            stickiness_mean = mean(stickiness),
            stickiness_IQR = IQR(stickiness), 
            stickiness_SD = sd(stickiness))

```

above chunk: 
generally low stickiness. 
higher stickiness for orig. agents (we have a potential explanation). 

next chunk: 
avg. over orig. & switch (investigating true model)

```{r}

#combined stickiness
df_true <- df1 %>%
  mutate(lose_global = agent_away + switch_away,
         all_global = agent_total + switch_total,
         stickiness = 1 - (lose_global / all_global)) %>%
  group_by(true_model) %>%
  summarize(stickiness_median = median(stickiness),
            stickiness_mean = mean(stickiness),
            stickiness_IQR = IQR(stickiness), 
            stickiness_SD = sd(stickiness))


```

above chunk: 
overfitting (even with BIC): Mod2 has much higher stickiness than
Mod13. Mod13 is almost down to 50%.

next chunk: 
investigating sigma: 

```{r}

#combined stickiness
df_sigma <- df1 %>%
  mutate(lose_global = agent_away + switch_away,
         all_global = agent_total + switch_total,
         stickiness = 1 - (lose_global / all_global)) %>%
  group_by(sigma) %>%
  summarize(stickiness_median = median(stickiness),
            stickiness_mean = mean(stickiness),
            stickiness_IQR = IQR(stickiness), 
            stickiness_SD = sd(stickiness))

```

above chunk: 
sigma is everything (as per fucking usual).

next chunk: 
combining parameters (interaction effects).

```{r}
#combined stickiness
df_SigMod <- df1 %>%
  mutate(lose_global = agent_away + switch_away,
         all_global = agent_total + switch_total,
         stickiness = 1 - (lose_global / all_global)) %>%
  group_by(sigma, true_model) %>%
  summarize(stickiness_median = median(stickiness),
            stickiness_mean = mean(stickiness),
            stickiness_IQR = IQR(stickiness), 
            stickiness_SD = sd(stickiness))

```

above chunk: 
sigma is the "strongest" variable (I.e., for both models low sigma = high stick).
However, there is an interaction in the sense that in high sigma conditions
the complex model does much worse. 

next chunk: 



