---
title: "prep_BA_reworkLOOP"
author: "Victor Møller"
date: "November 14, 2019"
output: html_document
---
________
This document tests and prepares all the data for the second paper. This includes four distinct sections:
1. Screening the data 
2. Preprocessing the files
3. Testing of the sampling of the different agent types and how much agents use the 6th step
4. Recording outcome measures for tables and plots. 

```{r}

#packages
library(pacman)
p_load(tidyverse, tidyselect, data.table)

```

### SCREENING ###

First screening: What files are in the folder for the raw data?

```{r}

#Working directory of RAW data. 
setwd("~/CRUST-1/Paper2/data/raw/csv")

#which files do we have
files = list.files(pattern=c("*.csv"), full.names=TRUE)

#do we lack anything 

#networks
identifiers <- c("Small", "Lattice", "TOM", "PT", 
              "_Mave_", "_Tess_", "_All_", "_Bo_",
              "_0.2_", "_0.5_", "_0.8_", 
              "_413_", "_484_",
              "_2_", "_7_", "_13_",
              "_COLAB", "_NOLAB")

for (i in identifiers){
  
network <- noquote(i)

#quick check: 
x <- files
network <- str_detect(files, i)
subset <- x[network]
value <- length(unlist(subset))
print(paste0(value, ": ", i))

}


```


Second screening: sanity checks  

```{r}

#Naming scheme:
naming_scheme <- "_Paper2.csv"

#Working directory of RAW data. 
setwd("~/CRUST-1/Paper2/data/raw/csv")

#for basic tests
condition <- list()
network <- list()
population <- list()
sigma <- list()
true_model <- list()
replica <- list()

#for other tests 
studiesMAX <- list()
studiesMIN <- list()

#the masterlist
masterlist <- list()

#your files 
files = list.files(pattern=c("*.csv"), full.names=TRUE)

#running the function
datacheck <- function(i){
  
  for(i in files){
    
  #reading data
  data <- read_csv(i)
  data <- na.omit(data)
  data <- tibble::as_tibble(data)
  
  #factorizing 
  data <- data %>%
  mutate(network = factor(network),
         population = factor(population),
         sigma = factor(sigma),
         net_size = factor(net_size),
         true_model = factor(true_model),
         colab_cond = factor(colab_cond),
         orig_type = factor(orig_type),
         strategy = factor(strategy))
  
  #basic tests 
  condition[i] <- paste0(i)
  network[i] <- levels(data$network)
  population[i] <- levels(data$population)
  sigma[i] <- levels(data$sigma)
  true_model[i] <- levels(data$true_model)
  replica[i] <- sum(unique(data$replica))
  
  #more tests 1: all replicas 10,000. 
  check <- data %>%
  group_by(replica, network, population, sigma, true_model,
          net_size, colab_cond) %>%
  summarize(stud = max(studies))
  
  studiesMAX[i] <- min(check$stud) #10,000
  studiesMIN[i] <- max(check$stud) #10,000
  
  }
  
  masterlist <- list(network, population, sigma,
                     true_model, replica, studiesMAX, studiesMIN)
  return(masterlist)
  
}

test <- datacheck(files)

## taking out parameters 
network <- unname(unlist(test[[1]]))
population <- unname(unlist(test[[2]]))
sigma <- unname(unlist(test[[3]]))
true_model <- unname(unlist(test[[4]]))
replica <- unname(unlist(test[[5]]))
studiesMAX <- unname(unlist(test[[6]]))
studiesMIN <- unname(unlist(test[[7]]))

#checking
network
population
sigma
true_model
replica
studiesMAX
studiesMIN

```

### PREPROCESSING ###

NA-omitting and restructuring the data

```{r}

#Working directory of RAW data. 
setwd("~/CRUST-1/Paper2/data/raw/csv")

#your files 
files = list.files(pattern=c("*.csv"), full.names=TRUE)

#the function
datawrite <- function(i){
  
  for(i in files){
  
  #where your raw files are:   
  setwd("~/CRUST-1/Paper2/data/raw/csv")
    
  #reading data:
  data <- read_csv(i)
  data <- na.omit(data)
  data <- tibble::as_tibble(data)
  
  #factorizing (might not work anyways): 
  data <- data %>%
  mutate(network = factor(network),
         population = factor(population),
         sigma = factor(sigma),
         net_size = factor(net_size),
         true_model = factor(true_model),
         colab_cond = factor(colab_cond),
         orig_type = factor(orig_type),
         strategy = factor(strategy))
  
  #directory for the files: 
  setwd("~/CRUST-1/Paper2/data/preprocessed")
  
  #write csv:
  write_csv(data, paste0(i))
  
  }
}

datawrite(files)

```

### SAMPLING ###

Data preparation for model sampling: 

```{r}

#Naming scheme:
naming_scheme <- "_Paper2.csv"

#working directory
setwd("~/CRUST-1/Paper2/data/preprocessed")
path = "~/CRUST-1/Paper2/data/preprocessed"
files <- list.files(path = path, pattern = "*.csv")


#initializing empty list 
datalist1 <- list()
datalist2 <- list()

samplingFX <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
            "strategy",
            "orig_type", #needed directly
            "old_model", #needed directly
            "selected_model") #needed directly 
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(strategy = factor(strategy),
          orig_type = factor(orig_type),
          old_model = factor(old_model),
          selected_model = factor(selected_model))
    
    #any sampling of own models? 
    df_errors <- df %>%
        filter(strategy != "colab") %>%
        group_by(orig_type) %>%
        summarize(count = sum(old_model == selected_model))
    
    #sampling distributions 
    df_sampling <- df %>%
        filter(strategy == "research") %>%
        group_by(orig_type, old_model, selected_model) %>%
        summarize(count = n())
    
    datalist1[i] <- list(df_errors)
    datalist2[i] <- list(df_sampling)
  }
    
  df_errors <- do.call("rbind", datalist1)
  df_sampling <- do.call("rbind", datalist2)
  
  #directory for the files: 
  setwd("~/CRUST-1/Paper2/data/sampling")
  
  #write csv:
  write_csv(df_errors, paste0("df_errors", naming_scheme))
  write_csv(df_sampling, paste0("df_sampling", naming_scheme))

}

#calling the function
samplingFX(files)

```

Data preparation for differential usage of 6th step.


```{r}

#Naming scheme:
naming_scheme <- "_Paper2.csv"

## prep: 
setwd("~/CRUST-1/Paper2/data/preprocessed")
path = "~/CRUST-1/Paper2/data/preprocessed"
files <- list.files(path = path, pattern = "*.csv")

#initializing empty list 
datalist1 <- list()
datalist2 <- list()

sixthFX <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
                "network",
                "strategy",
                "colab_cond",
                "switch_all",
                "switch_testing",
                "orig_agents") 
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(strategy = factor(strategy), 
           network = factor(network),
           colab_cond = factor(colab_cond))
    
    #overall number of switch_all & switch_testing
    overall <- df %>%
      group_by(network, colab_cond) %>%
      summarise(switch_all = sum(switch_all),
                switch_testing = sum(switch_testing),
                orig_agents = sum(orig_agents))
    
    #number of switch_all & switch_testing for strategy == colab
    colab <- df %>%
    filter(strategy == "colab") %>%
      group_by(network, colab_cond) %>%
      summarise(switch_all = sum(switch_all),
                switch_testing = sum(switch_testing),
                orig_agents = sum(orig_agents))
    
    datalist1[i] <- list(overall)
    datalist2[i] <- list(colab)
  }
    
  overall <- do.call("rbind", datalist1)
  colab <- do.call("rbind", datalist2)
  
  #directory for the files: 
  setwd("~/CRUST-1/Paper2/data/sampling")
  
  #write csv:
  write_csv(overall, paste0("sixth_overall", naming_scheme))
  write_csv(colab, paste0("sixth_colab", naming_scheme))

}

#calling the function
sixthFX(files)

```

### OUTCOME VARIABLES ###


Outcome variables for tables and plots 

```{r}
#Naming scheme:
naming_scheme <- "_Paper2.csv"

#working directory. 
setwd("~/CRUST-1/Paper2/data/preprocessed")
path = "~/CRUST-1/Paper2/data/preprocessed"
files <- list.files(path = path, pattern="*.csv")


#initializing empty list 
datalist1 <- list()
datalist2 <- list()

Outcomes <- function(files){
  
  #selecting cols (check )
    mycols <- c("replica", 
            "turn", 
            "studies", 
            "network", 
            "population", 
            "sigma",
            "colab_cond",
            "net_size",
            "true_model",
            "strategy",
            "switch_rep_study",
            "switch_rep",
            "init_g_true", #count of true orig. (testing) agents.
            "final_g_true", #count of post stud. (testing) agents. 
            "switch_true",
            "switch_true_changing",
            "orig_agents",
            "switch_testing",
            "prop_true",
            "prop_t_mod")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model),
          strategy = factor(strategy))
    
    stickiness <- df %>%
      filter(prop_t_mod == 0) %>%
      group_by(replica, sigma, population, network, true_model,
           net_size, colab_cond) %>%
      summarize(agent_away = sum(as.numeric(init_g_true == 1 & 
                                        final_g_true == 0)),
            agent_total = sum(as.numeric(init_g_true == 1)),
            switch_away = sum(switch_true_changing),
            switch_total = sum(switch_true),
            stickiness_agent = 1 - (agent_away / agent_total),
            stickiness_switch = 1 - (switch_away / switch_total),
            lose_global = agent_away + switch_away,
            all_global = agent_total + switch_total,
            stickiness_overall = 1 - (lose_global / all_global)) %>%
      select(-c(lose_global, all_global, agent_away, agent_total,
                switch_away, switch_total))
    
    fptt <- df %>%
        group_by(replica, population, network, sigma, true_model, net_size, 
           colab_cond) %>% 
        summarize(first_row = min(which(final_g_true > init_g_true)),
            first_study = studies[first_row],
            orig_agents = orig_agents[first_row],
            switch_testing = switch_testing[first_row],
            extra_agents = orig_agents - 1,
            FPTT = first_study - ((extra_agents / 2) + switch_testing)) %>%
      select(-c(first_row, first_study, orig_agents, 
                switch_testing, extra_agents))
    
    #create DF. 
    df_basic <- df %>%
      mutate(TAT_50 = ifelse(prop_true >= 0.5, 1, 0)) %>%
        group_by(replica, network, population, sigma, true_model,
          net_size, colab_cond) %>%
        summarize(RR = sum(switch_rep) / 
              sum(switch_rep_study),
              TAT = mean(prop_true),
              TAT_50 = mean(TAT_50)) 
    
    #grouping by strategy 
    df_strat <- df %>%
      mutate(TAT_50 = ifelse(prop_true >= 0.5, 1, 0)) %>%
        group_by(replica, network, population, sigma, true_model,
          net_size, colab_cond, strategy) %>%
        summarize(RR = sum(switch_rep) / 
              sum(switch_rep_study),
              TAT = mean(prop_true),
              TAT_50 = mean(TAT_50))
    
    stickiness_strat <- df %>%
      filter(prop_t_mod == 0) %>%
      group_by(replica, sigma, population, network, true_model,
           net_size, colab_cond, strategy) %>%
      summarize(agent_away = sum(as.numeric(init_g_true == 1 & 
                                        final_g_true == 0)),
            agent_total = sum(as.numeric(init_g_true == 1)),
            switch_away = sum(switch_true_changing),
            switch_total = sum(switch_true),
            stickiness_agent = 1 - (agent_away / agent_total),
            stickiness_switch = 1 - (switch_away / switch_total),
            lose_global = agent_away + switch_away,
            all_global = agent_total + switch_total,
            stickiness_overall = 1 - (lose_global / all_global)) %>%
      select(-c(lose_global, all_global, agent_away, agent_total,
                switch_away, switch_total))
    
    fptt_strat <- df %>%
        group_by(replica, population, network, sigma, true_model, net_size, 
           colab_cond, strategy) %>% 
        summarize(first_row = min(which(final_g_true > init_g_true)),
            first_study = studies[first_row],
            orig_agents = orig_agents[first_row],
            switch_testing = switch_testing[first_row],
            extra_agents = orig_agents - 1,
            FPTT = first_study - ((extra_agents / 2) + switch_testing)) %>%
      select(-c(first_row, first_study, orig_agents, 
                switch_testing, extra_agents))

    
    df_outcomes <- Reduce(function(x,y) merge(x, y, all = T), list(df_basic, stickiness, fptt))
    df_outcomes_strat <- Reduce(function(x,y) merge(x, y, all = T), list(df_strat, stickiness_strat, fptt_strat))
    
    datalist1[i] <- list(df_outcomes)
    datalist2[i] <- list(df_outcomes_strat)
  }
    
  df <- do.call("rbind", datalist1)
  df_strat <- do.call("rbind", datalist2)
  
  #directory for files (outcome)
  setwd("~/CRUST-1/Paper2/data/OutcomeMeasures")
  write_csv(df, paste0("outcomes", naming_scheme))
  write_csv(df_strat, paste0("outcomesStrat", naming_scheme))

}

#calling the function
Outcomes(files)

```

### FOR PLOTTING ###

true_false plot - only true:

```{r}

#Naming scheme:
naming_scheme <- "_Paper2.csv"

#working directory. 
setwd("~/CRUST-1/Paper2/data/preprocessed")
path = "~/CRUST-1/Paper2/data/preprocessed"
files <- list.files(path = path, pattern="*.csv")

#initializing empty list 
datalist <- list()

true_false_rework <- function(files){
  
  #selecting cols (check )
    mycols <- c("population", 
            "sigma",
            "true_model",
            "studies",
            "network",
            "net_size",
            "replica",
            "colab_cond",
            "prop_true")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model))
    
    #downsampling
    df <- df[seq(1, nrow(df), 50), ]
    
    
    #melting the variables
    naming <- colnames(df)
    
    #data
    df <- df %>%
    melt(id = c(naming[1:8])) %>% 
    mutate(true = ifelse(variable == "prop_true", "True", "False")) %>% 
    mutate(variable = relevel(variable, ref = "prop_true")) %>% 
    mutate(variable = fct_rev(variable)) 
    
    datalist[i] <- list(df)
  }
    
  df_final <- do.call("rbind", datalist)
  
  #directory for the files: 
  setwd("~/CRUST-1/Paper2/data/outcomeMeasures")
  
  #write csv:
  write_csv(df_final, paste0("TF_only_true", 
                             naming_scheme))
}

#calling the function
true_false_rework(files)

```

true_false with false 

```{r}

#Naming scheme:
naming_scheme <- "_Paper2.csv"

#working directory. 
setwd("~/CRUST-1/Paper2/data/preprocessed")
path = "~/CRUST-1/Paper2/data/preprocessed"

#initializing empty list 
datalist <- list()

true_false_CON <- function(files, identifier){

  #selecting cols (check )
    mycols <- c("population", 
            "sigma",
            "true_model",
            "studies",
            "network",
            "net_size",
            "replica",
            "colab_cond",
            "prop_1",
            "prop_2",
            "prop_3",
            "prop_4",
            "prop_5",
            "prop_6",
            "prop_7",
            "prop_8",
            "prop_9",
            "prop_10",
            "prop_11",
            "prop_12",
            "prop_13",
            "prop_14",
            "prop_true")
  
  for(i in files){

    #read csv 
    df <- read_csv(i)[mycols]
    
    #as factor
    df <- df %>%
    mutate(network = factor(network),
          population = factor(population),
          sigma = factor(sigma),
          colab_cond = factor(colab_cond),
          net_size = factor(net_size),
          true_model = factor(true_model))
    
    #downsampling
    df <- df[seq(1, nrow(df), 50), ]
    
    
    #melting the variables
    naming <- colnames(df)
    df <- df %>%
    melt(id = c(naming[1:8])) %>%
    mutate(true = ifelse(variable == "prop_true", "True", "False")) %>% 
    mutate(variable = relevel(variable, ref = "prop_true")) %>% 
    mutate(variable = fct_rev(variable)) 
    
    datalist[i] <- list(df)
  }
    
  df_final <- do.call("rbind", datalist)
  
  #directory for the files: 
  setwd("D:/data/MetaScience_BA_FINAL/dataPlotting")
  
  #write csv:
  write_csv(df_final, paste0(identifier, "_true_false_CON",
                             naming_scheme))

}

#Subsetting for the different networks
subset_variables <- c("Lattice", "Small", "PT", "TOM")

for (i in subset_variables){
  
  #update working directory 
  setwd("~/CRUST-1/Paper2/data/preprocessed")
  path = "~/CRUST-1/Paper2/data/preprocessed"
  
  files <- list.files(path = path, pattern=paste0("^", i, ".*.csv"))
  
  true_false_CON(files, i)
}


```
