---
title: "Untitled"
author: "Victor Møller"
date: "25 maj 2019"
output: html_document
---

14-09-2019
This document tests & cleans data from ABM5. 
It is probably only going to work for test-phase with small
amounts of data. It takes data from "new_data" folder and outputs to "tests".

```{r}
#set working directory to where you have raw files
setwd("C:/Users/victm/Dropbox/CogSci 4/Social and Cultural Dynamics in Cognition/exam/CRUST-1/data/new_data")

#packages
library(pacman)
p_load(tidyverse, tidyselect)

```

Loading data

```{r}

#file-names
temp <- list.files(pattern="*csv")

#loading them 
for(i in 1:length(temp)) assign(temp[i], read.csv(temp[i], sep = ";"))

#bind all together - coerces something into character. 
data <- mget(ls(pattern="*csv")) %>%
              bind_rows()

#remove all the old shit 
rm(list=setdiff(ls(), "data")) 

```

Naive tests in sequential order. 
Just testing whether we have the right data. 

Notes: 
- network: currently a character (it this what we want?)
- population: currently a character (is this what we want?)

```{r}

summary(data$turn) #max should be whatever max is set to (check ABM2 for input)
unique(data$network) #Lattice, Small 
unique(data$population) #All, Bo, Mave, Tess
summary(data$sigma) #min: 0.2, mean: 0.5, max: 0.8
summary(data$sample_size) #min: 20, mean: 60, max: 100
summary(data$true_model) #min: 2, mean: 7.33!!, max: 13. 
summary(data$strategy) #Bo, Mave, Tess (should be more or less equal). 

```

More sophisticated tests. 
Comments reflect expected output (if code is working as it should).

```{r}

#Check 1 
all(data$edges_testing == data$edges_not_same_global) #TRUE

#Check 2 (not true at the moment since we have changed edges_total).
#There is no bug in the code, we just need to consider what we want. 
data_check <- data %>%
  mutate(together = edges_same_global + edges_not_same_global)
all(data_check$edges_total == data_check$together) #TRUE

#Check 3. 
#Split into true models & Check whether it is correctly assigned. 
data2 <- data_check %>%
  filter(true_model == 2)

data7 <- data_check %>%
  filter(true_model == 7)

data13 <- data_check %>%
  filter(true_model == 13)

all(data2$proportion_2 == data2$proportion_true) #TRUE
all(data7$proportion_7 == data7$proportion_true) #TRUE
all(data13$proportion_13 == data13$proportion_true) #TRUE

#check 4
sum(data[37:50]) #same as number of rows. 

#check 5
all(data$edges_testing >= data$edges_changing) #TRUE 

#check 6.
#overwrites the old "data_check" which is fine.  
data_check <- data %>%
  mutate(replica_stud = edges_replicated + edges_not_replicated)

all(data_check$edges_replication_study == data_check$replica_stud) #TRUE 

#check 7
data_check <- data_check %>%
  mutate(edges_already_test = edges_already_true_changing + edges_already_true_rejecting)
  
all(data_check$edges_already_test == data_check$edges_already_true) #TRUE 

```

Filtering columns. 

#columns that we don't use in the analsis but kept from the Devezer paper. 
--> beta1_true 
--> beta1_estimate
--> beta1_error
--> tStatistics
--> RSQ
--> ARSQ
--> AIC
--> BIC

#columns that were used as sanity checks. 
--> edges_not_same_global
--> edges_not_replicated
--> edges_already_true_rejecting 

```{r}

#selecting the columns we want. 
cols <- c("beta1_true", 
            "beta1_estimate",
            "beta1_error",
            "tStatistics",
            "RSQ",
            "ARSQ",
            "AIC",
            "BIC",
            "edges_not_same_global",
            "edges_not_replicated",
            "edges_already_true_rejecting",
            "edges_same_global")

data <- data %>%
  dplyr::select(-one_of(cols)) 

#BE CAREFUL, YOU ARE DELETING DATA!!
data <- data %>%
  subset(studies <= 11000)

#checking whether it worked
data_check <- data %>%
  group_by(replica, sigma, population) %>%
  summarize(studymax = max(studies))
  
#changing column index (hacky but works)
col_start <- 1:20
col_end <- 21:41
col_great <- 42

data <- data[, c(1:20, 42, 21:41)]
colnames(data)

```

new working directory & writing files.

```{r}

#output directory - NOW TESTS.
setwd("C:/Users/victm/Dropbox/CogSci 4/Social and Cultural Dynamics in Cognition/exam/CRUST-1/data/tests")

getwd()
write.csv(data, "breaking_points.csv", row.names = FALSE)

```


