---
title: "Untitled"
author: "Victor Møller"
date: "25 maj 2019"
output: html_document
---

Files loaded in from outside storage space. 
This is where the working directory is refering. 

```{r}
#set working directory to where you have raw files
setwd("D:/soc_kult_exam/data raw/model2csv")

#packages
library(tidyverse)

```

Loading Lattice

```{r}

#file-names
temp <- list.files(pattern="Lattice")

#loading them 
for(i in 1:length(temp)) assign(temp[i], read.csv(temp[i], sep = ";"))

#bind all latice together. 
lattice <- mget(ls(pattern="Lattice")) %>%
              bind_rows()

#remove all the old shit 
rm(list=setdiff(ls(), "lattice")) #lattice_all_0.8 lacking turn 14. 


```

checking small world.
The comments reflect the expected print. 

```{r}

#check 1 
all(lattice$edges_testing == lattice$edges_not_same_global) #TRUE

#check 2
lattice_checking <- lattice %>%
  mutate(together = edges_same_global + edges_not_same_global)

all(lattice_checking$edges_total == lattice_checking$together) #TRUE

#check 3. 
#Set "true_model" = the true model you are working with. 
small_mod <- lattice %>%
  filter(true_model == 2) 

all(small_mod$proportion_2 == small_mod$proportion_true) #TRUE

#check 4
sum(lattice[37:50]) #6.600.000

#check 5
all(lattice$edges_testing >= lattice$edges_changing) #TRUE 

#check 6.
#overwrites the old "small_checking" but that is fine. 
lattice_checking <- lattice %>%
  mutate(replica_stud = edges_replicated + edges_not_replicated)

all(lattice_checking$edges_replication_study == lattice_checking$replica_stud) #TRUE 

#check 7
lattice_checking <- lattice_checking %>%
  mutate(edges_already_test = edges_already_true_changing + edges_already_true_rejecting)
  
all(lattice_checking$edges_already_test == lattice_checking$edges_already_true) #TRUE 

```

Filtering columns. 

#columns that we don't use in the analsis but kept from the Devezer paper. 
--> beta1_true 
--> beta1_estimate
--> beta1_error
--> tStatistics
--> RSQ
--> ARSQ
--> AIC
--> BIC

#columns that were used as sanity checks. 
--> edges_not_same_global
--> edges_not_replicated
--> edges_already_true_rejecting 

```{r}

#selecting the columns we want. 
lattice <- lattice %>%
  select(-c(beta1_true, 
            beta1_estimate,
            beta1_error,
            tStatistics,
            RSQ,
            ARSQ,
            AIC,
            BIC,
            edges_not_same_global,
            edges_not_replicated,
            edges_already_true_rejecting,
            edges_same_global))

#subsetting 
lattice <- lattice %>%
  subset(studies <= 11000)

#checking whether it worked
lattice_check <- lattice %>%
  group_by(replica, sigma, population) %>%
  summarize(studymax = max(studies))
  
#changing column index (hacky but works)
col_start <- 1:20
col_end <- 21:41
col_great <- 42

lattice <- lattice[, c(1:20, 42, 21:41)]
colnames(lattice)

```

new working directory & writing files.

```{r}

#output directory 
setwd("C:/Users/victm/Dropbox/CogSci 4/Social and Cultural Dynamics in Cognition/exam/CRUST-1/data/ABMdata/ABMcsv")

getwd()
#write csv. 
#write.csv(lattice, "lattice_sanity.csv", row.names = FALSE)
write.csv(lattice, "lattice_2.csv", row.names = FALSE)

```


