---
title: "abmTOM"
author: "Mikkel Werling & Victor Moeller"
date: "5/16/2019"
output: html_document
---

Updated on 31-10-2019.
Now up to the changes made in the rework-session. New constants, fewer variables. This is the document for the TOM-networks and 484-sized networks in general. 


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

packages

```{r}
library(pacman)

p_load(igraph, stringr, ggraph, wesanderson, cowplot, caTools, data.table, permute, matrixStats, MCMCpack, tidyverse, rlist, nnet)

```

paths

```{r}
baseDir <- "~/CRUST-1" #the "." stopped working. 
scriptDir <- paste0(baseDir, "/FunctionsLoads/Functions")
inputDir <- paste0(baseDir, "/Paper2/data")
outputDirCsv <- paste0(baseDir, "/Paper2/data/raw/csv")
outputDirRds <- paste0(baseDir, "/Paper2/data/raw/rds")
```

functions

```{r}
source(paste0(scriptDir, "/analysis.R"))
source(paste0(scriptDir, "/calculateDet.R"))
source(paste0(scriptDir, "/calculateDistance.R"))
source(paste0(scriptDir, "/compareModels.R"))
source(paste0(scriptDir, "/constantsPaper2.R")) #new constants baby.
source(paste0(scriptDir, "/convertBinary.R"))
source(paste0(scriptDir, "/generateBetas.R"))
source(paste0(scriptDir, "/generateModels.R"))
source(paste0(scriptDir, "/generateXSet.R"))
source(paste0(scriptDir, "/generateY.R"))
source(paste0(scriptDir, "/getBetas.R"))
source(paste0(scriptDir, "/getPredictors.R"))
source(paste0(scriptDir, "/modelSimilarByInteractionRework.R"))
source(paste0(scriptDir, "/modelSimilarByTermRework.R"))
source(paste0(scriptDir, "/modelToStr.R"))
source(paste0(scriptDir, "/searchModel.R"))
source(paste0(scriptDir, "/seedGenerator.R"))
source(paste0(scriptDir, "/strToModel.R"))
source(paste0(scriptDir, "/abmPaper2TOM.R")) 
```

modelsString, g & agentTurn

```{r}

#some models -  
load(paste0(baseDir, "/FunctionsLoads/Loads/modelsString"))

```

input parameters

```{r}

## Number of replications
replications <- 1 #100 originally, now 2. 

## Length of the simulation
turns <- 1000
study_cap <- 1000

## Number of factors
k <- 3

## generating 
load(paste0(baseDir, "/FunctionsLoads/Loads/models")) #changed

## Identify the number of predictors of each model
predictors <- getPredictors(models)

## Generate Betas
weights <- generateBetas(models)

## Correlation
correlation <- 0.2

## modelCompare & selection
modelSelection <- "hard"

## ndec
ndec = 4

## outputs
outputFile <- ".csv" 
paramFile <- ".rds"

## verbose
verbose <- TRUE
```

For output. 
These are the parameters we don't vary. 

```{r}
net_size <- 484

```

setting seeds

```{r}
seeds <- seedGenerator(replications, paste0(inputDir, "/seeds.csv"))

```

FULL RUN: 
defining parameters: 
net_types: "Lattice", "Small", "TOM"
sigmas: 0.2, 0.5, 0.8 (can be anything)
base_sampleSizes: 20, 100 (can be anything)
pop_types: "Bo", "Tess", "Mave", "All"
tModes: 2, 7, 13 (can be any of the 14 models)
modelCompares: BIC, AIC 
colab_probs: 0, 0.02 (can be anything between 0 and 1)

```{r}
net_types <- list("Lattice", "Small", "TOM") #"Lattice", "Small", "TOM"
sigmas <- list(0.2, 0.5, 0.8) #0.2, 0.5, 0.8 
base_sampleSizes <- list(20, 100) #20, 100. 
pop_types <- list("Bo", "Mave", "Tess", "All") #"Bo", "Mave", "Tess", "All"
tMods <- list(2, 7, 13) #2, 7, 13. 
modelCompares <- list(AIC, BIC) #AIC, BIC 
colab_probs <- list(0, 0.02) #no colab vs. colab. 

```

```{r}

start_time <- Sys.time()

### running the ABM for all combinations of parameters ### 

for(net_type in net_types){ 
  for(sigma in sigmas){
    for(base_sampleSize in base_sampleSizes){
      for(pop_type in pop_types){
        for(tMod in tMods){ #not sure this works. 
          for(modelCompare in modelCompares){ #should be
            for(colab_prob in colab_probs){
        
abmTOM(replications, turns, models, k, 
    weights, base_sampleSize, correlation, sigma,
    modelCompare, modelSelection, inputDir, outputDir, outputFile, paramFile,
    verbose, ndec, seeds, modelsString)
            }
          }
        }
      }
    }
  }
}

end_time <- Sys.time()
end_time - start_time

```
