---
title: "Untitled"
author: "Victor Møller"
date: "November 7, 2019"
output: html_document
---

Using R for functions:
https://dplyr.tidyverse.org/articles/programming.html

1. Tidyverse is not referentially transparent

```{r}
library(tidyverse)

# works
df <- tibble(x = 1:3, y = 3:1)
filter(df, x == 1)

# does not work 
my_var <- x
filter(df, my_var == 1)

# does not work
my_var <- "x"
filter(df, my_var == 1)

```

2. other domains / strings

```{r}

# does not work 
greet <- function(name) {
  "How do you do, name?"
}
greet("Hadley")

# does work 
greet <- function(name) {
  paste0("How do you do, ", name, "?")
}
greet("Hadley")

# does work
greet <- function(name) {
  glue::glue("How do you do, {name}?")
}
greet("Hadley")

```

3. repeated code 

```{r}

mutate(df1, y = a + x)
mutate(df2, y = a + x)
mutate(df3, y = a + x)
mutate(df4, y = a + x)

mutate_y <- function(df){
  mutate(df, y = a + x)
}

mutate_y(df1, df2, df3, df4)

# the issue - variables in global env. & not in local
df1 <- tibble(x = 1:3)
a <- 10
mutate_y(df1)

# a fix - gives the error if it occurs 
mutate_y <- function(df) {
  mutate(df, y = .data$a + .data$x)
}

mutate_y(df1)

```

4. different expressions.
The issue: dplyr automatically quotes input variables (like: y).

```{r}

# making a tibble
df <- tibble(
  g1 = c(1, 1, 2, 2, 2),
  g2 = c(1, 2, 1, 2, 1),
  a = sample(5),
  b = sample(5)
)

# what we want to automize
df %>%
  group_by(g1) %>%
  summarise(a = mean(a))

# what we want to automize
df %>%
  group_by(g2) %>%
  summarise(a = mean(a))

# does not work 
my_summarise <- function(df, group_var) {
  df %>%
    group_by(group_var) %>%
    summarise(a = mean(a))
}

my_summarise(df, g1)
my_summarise(df, "g2")

#notice that group var is in quotation for both cases. 
```

5. quo()
quo() returns a quosure. 
!! unquotes (so that group_by does not do it).

```{r}

#how it works 
quo(g1)
quo(a + b + c)
quo("a")

# using it (still same error)
my_summarise(df, quo(g1))

# working function
my_summarise <- function(df, group_var) {
  df %>%
    group_by(!! group_var) %>%
    summarise(a = mean(a))
}

my_summarise(df, quo(g1))

```

6. making it smooth. 
The function does not understand that we are giving it an argument
which does not refer to any object (in global env.)

```{r}

# wrong solution
my_summarise <- function(df, group_var) {
  quo_group_var <- quo(group_var)
  print(quo_group_var)

  df %>%
    group_by(!! quo_group_var) %>%
    summarise(a = mean(a))
}

my_summarise(df, g1) # 'group_var' again. 
#quo() is being too literal (it returns what is there, not the sup. var.)

```

7. enquo() takes what is typed and returns quosure. 
This works as we 
(1) we enquo() and thus get the quosure.
(2) we use !! to unquote that quosure. 

```{r}

my_summarise <- function(df, group_var) {
  group_var <- enquo(group_var)
  print(group_var)

  df %>%
    group_by(!! group_var) %>%
    summarise(a = mean(a))
}

my_summarise(df, g1)

```

8. Different grouping variables 

```{r}
#what we want 
summarise(df, mean = mean(a), sum = sum(a), n = n())
summarise(df, mean = mean(a * b), sum = sum(a * b), n = n())

#testing approaches (quo, works). 
my_var <- quo(a)
summarise(df, mean = mean(!! my_var), sum = sum(!! my_var), n = n())

#tool for debugging (how does dplyr understand the code)
quo(summarise(df,
  mean = mean(!! my_var),
  sum = sum(!! my_var),
  n = n()
))

#functions with enquo
my_summarise2 <- function(df, expr) {
  expr <- enquo(expr) #as we don't want ^expr but whatever we input. 

  summarise(df,
    mean = mean(!! expr),
    sum = sum(!! expr),
    n = n()
  )
}
my_summarise2(df, a)
my_summarise2(df, a * b)

```

9. Different input & output variables. 
quo_name() convers to a string

```{r}

#what we want
mutate(df, mean_a = mean(a), sum_a = sum(a))
mutate(df, mean_b = mean(b), sum_b = sum(b))

#how we do it
my_mutate <- function(df, expr) {
  expr <- enquo(expr) #into quosure. 
  mean_name <- paste0("mean_", quo_name(expr)) #quo_name() into str. 
  sum_name <- paste0("sum_", quo_name(expr))

  mutate(df,
    !! mean_name := mean(!! expr), #out of quosure (unquote). 
    !! sum_name := sum(!! expr) #out of quosure (unquote).
  )
}

my_mutate(df, a)

#how I would do it (which does not work, not with := either). 
my_mutate <- function(df, expr) {
  expr <- enquo(expr) #into quosure. 
  mean_name <- paste0("mean_", quo_name(expr)) #quo_name() into str. 
  sum_name <- paste0("sum_", quo_name(expr))

  obj <- df %>%
    mutate(!! mean_name <- mean(!! expr), #out of quosure (unquote). 
           !! sum_name <- sum(!! expr)) #out of quosure (unquote).
}

my_mutate(df, a)

```

10. multiple variables
enquos() captures all elements. 
!!! splices all arguments in. 

```{r}

my_summarise <- function(df, ...) {
  group_var <- enquos(...)

  df %>%
    group_by(!!! group_var) %>%
    summarise(a = mean(a))
}

my_summarise(df, g1, g2)

# another !!! example
args <- list(na.rm = TRUE, trim = 0.25)
quo(mean(x, !!! args))

args <- list(quo(x), na.rm = TRUE, trim = 0.25)
quo(mean(!!! args))
```

11. quoting 

```{r}

disp ~ cyl + drat

#comp. value of expression
toupper(letters[1:5])

#returning expression
quote(toupper(letters[1:5]))

```

12. variables that look the same are different.

```{r}

f <- function(x) {
  quo(x)
}

x1 <- f(10)
x2 <- f(100)

#expr: same, env: different
x1
x2

#a nice package
library(rlang)

get_env(x1)
get_env(x2)

eval_tidy(x1)
eval_tidy(x2)

#why is this relevant?
user_var <- 1000
mtcars %>% summarise(cyl = mean(cyl) * user_var)

```

13. unquoting

```{r}

#capturing the expression
quo(toupper(letters[1:5]))

#capturing the value
quo(toupper(!! letters[1:5]))
quo(toupper(UQ(letters[1:5])))

#first specifying as var & then using stuff. 
var1 <- quo(letters[1:5])
quo(toupper(!! var1))


```

14. another way of structuring it.

```{r}
#making the function
my_mutate <- function(x) {
  mtcars %>%
    select(cyl) %>%
    slice(1:4) %>%
    mutate(cyl2 = cyl + (!! x))
}

#a new function which unquotes
f <- function(x) quo(x)

#generating unquoted expressions
expr1 <- f(100)
expr2 <- f(10)

my_mutate(expr1)
my_mutate(expr2) #the value is in the env. 

```

15. using UQ() instead of !!

```{r}
# the issue
my_fun <- quo(fun)
quo(!! my_fun(x, y, z))

# the solution
quo(UQ(my_fun)(x, y, z))

# where !! and UQ() are the same
my_var <- quo(x)
quo(filter(df, !! my_var == 1))
quo(filter(df, UQ(my_var) == 1))


```

16. unquote splicing 

```{r}

#splicing
quo(list(!!! letters[1:5]))

#vector and arg. names
x <- list(foo = 1L, bar = quo(baz))
quo(list(!!! x))

#args. 
args <- list(mean = quo(mean(cyl)), count = quo(n()))

#smooth..
mtcars %>%
  group_by(am) %>%
  summarise(!!! args)

```

:= operator (supports unquoting)

```{r}
mean_nm <- "mean"
count_nm <- "count"

mtcars %>%
  group_by(am) %>%
  summarise(
    !! mean_nm := mean(cyl),
    !! count_nm := n()
  )
```


```{r setup, include=FALSE}

install.packages("rlang")
library(rlang)
#what to group by: 
RR_TAT_FUN <- function(melted_frame, group_var){

  df <- enquo(melted_frame)
  group_var <- enquo(group_var)
  print(group_var)
  print(df)
  df2 := !! df
  print(df2)

}

RR_TAT_FUN(melt_RR_TAT, Sigma)


```
