---
title: "sigma plots for epi 0.5 across both networks"
author: "Mikkel Werling"
date: "5/21/2019"
output: html_document
---

14-09-2019
Adapted from "true_false" Rmd to accomodate new data format. 

```{r}
library(pacman)

p_load(igraph, stringr, ggraph, wesanderson, cowplot, caTools, data.table, permute, matrixStats, MCMCpack, tidyverse, ggunchained, tidyselect)
```

INTRODUCTION TO THE DOCUMENT:
1. Read data is obligatory
2. Downsampling is always recommendable, as it does not make any aesthetic difference, but significantly increases the computational load.
3. True/False plots for the individual conditions
4. Bo-plot for all the conditions with 14th and true model
5. Averaged plot of true_proportion for all the different populations 

read data

```{r}
setwd("C:/Users/victm/Dropbox/CogSci 4/Social and Cultural Dynamics in Cognition/exam/CRUST-1/data/tests")

df_new <- read.csv("two_runs_new.csv", sep = ",")
df_old <- read.csv("SocKult.csv", sep = ",")

mycols <- c("population", 
            "sigma",
            "true_model",
            "studies",
            "sample_size",
            "network",
            "proportion_1",
            "proportion_2",
            "proportion_3",
            "proportion_4",
            "proportion_5",
            "proportion_6",
            "proportion_7",
            "proportion_8",
            "proportion_9",
            "proportion_10",
            "proportion_11",
            "proportion_12",
            "proportion_13",
            "proportion_14",
            "proportion_true")

df_new <- df_new %>%
  dplyr::select(one_of(mycols)) 

df_old <- df_old %>%
  dplyr::select(one_of(mycols))

#downsampling
df_new <- df_new[seq(1, nrow(df_new), 30), ]
df_old <- df_old[seq(1, nrow(df_old), 30),]

```

#### COWPLOT APPROACH ####

melting for cowplot

```{r}

naming <- colnames(df_new)

melt_new <- df_new %>%
  melt(id = c(naming[1:6])) %>% #melting with proportions becoming variable and their values becoming values
  mutate(true_model = as.factor(true_model)) %>%
  mutate(true = ifelse(variable == "proportion_true", "True", "False")) %>% #making a identifying column in order to color for the plot
  mutate(variable = relevel(variable, ref = "proportion_true")) %>% #releveling so that proportion true is considered first
  mutate(variable = fct_rev(variable)) #releveling so that proportion true is considered last - this is done in order to make it the top layer in the overlay between different smooths.

naming <- colnames(df_old)
melt_old <- df_old %>%
  melt(id = c(naming[1:6])) %>% 
  mutate(true_model = as.factor(true_model)) %>%
  mutate(true = ifelse(variable == "proportion_true", "True", "False")) %>% 
  mutate(variable = relevel(variable, ref = "proportion_true")) %>% 
  mutate(variable = fct_rev(variable)) 


```

Plotting w. cowplot 

```{r}

#what you want to plot
sigma_p <- 0.5
population_p <- "All"
network_p <- "Lattice"
true_model_p <- 7
sample_size_p <- 20


g1 <- melt_new %>%
  filter(sigma == sigma_p, population == population_p, network == network_p, true_model == true_model_p, sample_size == sample_size_p) %>%
  ggplot(aes(studies, value, color = true))+
  geom_point(alpha = 0.1) +
  geom_smooth(method = "loess", se = F, alpha = 0.1, size = 1.2, aes(labels = variable)) +
  geom_hline(aes(yintercept = 0.5), color = "red", linetype = "dotted", size = 1) + 
  labs(x = "Studies", y = "Proportion", color = "Proportion of different models", 
       title = "Proportion of agents at the true model",
       subtitle = paste("Network:", network_p, "|", "Population:", population_p, "|", "Sigma:", sigma_p, "|", "True Model:", true_model_p)) +
  theme_janco_point()

network_p <- "Small"

g2 <- melt_new %>%
  filter(sigma == sigma_p, population == population_p, network == network_p, true_model == true_model_p, sample_size == sample_size_p) %>%
  ggplot(aes(studies, value, color = true))+
  geom_point(alpha = 0.1) +
  geom_smooth(method = "loess", se = F, alpha = 0.1, size = 1.2, aes(labels = variable)) +
  geom_hline(aes(yintercept = 0.5), color = "red", linetype = "dotted", size = 1) + 
  labs(x = "Studies", y = "Proportion", color = "Proportion of different models", 
       title = "Proportion of agents at the true model",
       subtitle = paste("Network:", network_p, "|", "Population:", population_p, "|", "Sigma:", sigma_p, "|", "True Model:", true_model_p)) +
  theme_janco_point()
  

g3 <- melt_old %>%
  filter(sigma == sigma_p, population == population_p, network == network_p, true_model == true_model_p, sample_size == sample_size_p) %>%
  ggplot(aes(studies, value, color = true))+
  geom_point(alpha = 0.1) +
  geom_smooth(method = "loess", se = F, alpha = 0.1, size = 1.2, aes(labels = variable)) +
  geom_hline(aes(yintercept = 0.5), color = "red", linetype = "dotted", size = 1) + 
  labs(x = "Studies", y = "Proportion", color = "Proportion of different models", 
       title = "Proportion of agents at the true model",
       subtitle = paste("Network:", network_p, "|", "Population:", population_p, "|", "Sigma:", sigma_p, "|", "True Model:", true_model_p)) +
  theme_janco_point()

plot_grid(g1, g2, g3)

```

### FACET APPROACH ###
only compares "small". 

```{r}
melt_new$ID <- "new"
melt_old$ID <- "old"

melt_all <- rbind(melt_new, melt_old)

sigma_p <- 0.5
population_p <- "Mave"
network_p <- "Small"
true_model_p <- 7
sample_size_p <- 100


g1 <- melt_all %>%
  filter(sigma == sigma_p, population == population_p, true_model == true_model_p, network == network_p, sample_size == sample_size_p) %>%
  ggplot(aes(studies, value, color = true))+
  geom_point(alpha = 0.01) +
  geom_smooth(method = "loess", se = F, alpha = 0.1, size = 1.2, aes(labels = variable)) +
  geom_hline(aes(yintercept = 0.5), color = "red", linetype = "dotted", size = 1) + 
  labs(x = "Studies", y = "Proportion", color = "Proportion of different models", 
       title = "Proportion of agents at the true model",
       subtitle = paste("Network:", network_p, "|", "Population:", population_p, "|", "Sigma:", sigma_p, "|", "True Model:", true_model_p)) +
  theme_janco_point() +
  facet_wrap(~ID)

g1

```

All populations comparison. 

```{r}

network_p <- "Small"
true_model_p <- 7
sample_size_p <- 100
sigma <- 0.5

melt_true <- melt_new %>%
  filter(true == "True")

g1 <- melt_true %>%
  filter(sigma == sigma_p, true_model == true_model_p, network == network_p, sample_size == sample_size_p) %>%
  ggplot(aes(studies, value, color = population))+
  geom_point(alpha = 0.01) +
  geom_smooth(method = "loess", se = F, alpha = 0.1, size = 1.2, aes(labels = variable)) +
  geom_hline(aes(yintercept = 0.5), color = "red", linetype = "dotted", size = 1) + 
  labs(x = "Studies", y = "Proportion", color = "Proportion of different models", 
       title = "Proportion of agents at the true model",
       subtitle = paste("Network:", network_p, "|", "All Populations", "|", "Sigma:", sigma_p, "|", "True Model:", true_model_p)) +
  theme_janco_point() +
  facet_wrap(~ID)

g1

```

All true models 

```{r}

network_p <- "Small"
population_p <- "All"
sample_size_p <- 100
sigma <- 0.5

g1 <- melt_true %>%
  filter(sigma == sigma_p, network == network_p, sample_size == sample_size_p, population == population_p) %>%
  ggplot(aes(studies, value, color = true_model))+
  geom_point(alpha = 0.01) +
  geom_smooth(method = "loess", se = F, alpha = 0.1, size = 1.2, aes(labels = variable)) +
  geom_hline(aes(yintercept = 0.5), color = "red", linetype = "dotted", size = 1) + 
  labs(x = "Studies", y = "Proportion", color = "Proportion of different models", 
       title = "Proportion of agents at the true model",
       subtitle = paste("Network:", network_p, "|", "All Populations", "|", "Sigma:", sigma_p, "|", "True Model:", true_model_p)) +
  theme_janco_point() +
  facet_wrap(~ID)

g1

```

