---
title: "models"
author: "Victor Møller"
date: "6 maj 2019"
output: html_document
---

reading data 

```{r}

stickiness <- read.csv("bayes/stickiness.csv")
meantime <- read.csv("bayes/meantime.csv")
timeto <- read.csv("bayes/timeto.csv")

```

making model for time to true

```{r}

#model call
mod_f <- bf("time_to_true ~ agent * network")
get_prior(mod_f, timeto, family = gaussian())

#running the model with regularizing priors 
ttt_mod <- brm(
  mod_f, 
  prior = c(
    prior(normal(4, 2), class = "Intercept"),
    prior(normal(0, 2), class = "b"),
    prior(normal(0, 2), class = "sigma")),
  data = timeto, 
  cores = 4, iter = 4000, warmup = 2000,
  sample_prior = TRUE, #added for later use. 
  file = "bayes/ttt_mod" #saving for later use - these models take ages to run. 
)

ttt_mod

```

making model for mean time

```{r}
#model call
mod_f <- bf("meantime ~ agent * network")
get_prior(mod_f, meantime, family = gaussian())

#running the model with regularizing priors 
tat_mod <- brm(
  mod_f, 
  prior = c(
    prior(normal(0, 2), class = "Intercept"),
    prior(normal(0, 2), class = "b"),
    prior(normal(0, 2), class = "sigma")),
  data = meantime, 
  cores = 4, iter = 4000, warmup = 2000,
  sample_prior = TRUE, #added for later use. 
  file = "bayes/tat_mod" #saving for later use - these models take ages to run. 
)

#summary stats
tat_mod
plot(tat_mod) 
```

making model for sticky

```{r}

#model call
mod_f <- bf("stickiness ~ agent * network")
get_prior(mod_f, stickiness, family = gaussian())

#running the model with regularizing priors 
stick_mod <- brm(
  mod_f, 
  prior = c(
    prior(normal(0, 2), class = "Intercept"),
    prior(normal(0, 2), class = "b"),
    prior(normal(0, 2), class = "sigma")),
  data = stickiness, 
  cores = 4, iter = 4000, warmup = 2000,
  sample_prior = TRUE, #added for later use. 
  file = "bayes/stick_mod" #saving for later use - these models take ages to run. 
)

#summary stats
stick_mod
plot(stick_mod) 

```

non-linear outcome variable for time to true (gamma distribution).
check gen_nonlinear & p. 15.
try with normal (gaussian).
the posterior is not looking good. 

```{r}

nltimeto <- read.csv("bayes/nltimeto.csv")

#model call
mod_f <- bf("time_to_true ~ agent * network")
get_prior(mod_f, nltimeto, family = gaussian())

#running the model with regularizing priors 
tttn_mod <- brm(
  mod_f, 
  family = gaussian(), #or what would be appropriate? 
  prior = c( #& what about priors?
    prior(normal(1, 1), class = "Intercept"),
    prior(normal(0, 1), class = "b"),
    prior(normal(0, 1), class = "sigma")), #using get_priors. 
  data = nltimeto, 
  cores = 4, iter = 4000, warmup = 2000, chains = 1,
  sample_prior = TRUE #added for later use. 
  #file = "bayes/tttn_mod" #saving for later use - these models take ages to run. 
)

#okay
tttn_mod

#the issue
pp_check(tttn_mod)

```

This seems crazy.
Can it be specified in model call or with a link that makes sense?
Is it close to a log?
still not super good. 

```{r}

nltimeto <- nltimeto %>%
  mutate(log_time = log(time_to_true))

mean(nltimeto$log_time)

#model call
mod_f <- bf("log_time ~ agent * network")
get_prior(mod_f, nltimeto, family = gaussian())

#running the model with regularizing priors 
tttg_mod <- brm(
  mod_f, 
  family = gaussian(), #or what would be appropriate? 
  prior = c( #& what about priors?
    prior(normal(0, 1), class = "Intercept"),
    prior(normal(0, 1), class = "b"),
    prior(normal(0, 1), class = "sigma")), #using get_priors. 
  data = nltimeto, 
  cores = 4, iter = 4000, warmup = 2000, chains = 1,
  sample_prior = TRUE #added for later use. 
  #file = "bayes/tttg_mod" #saving for later use - these models take ages to run. 
)

#This is slightly better. 
tttg_mod
pp_check(tttg_mod)

```

Trying with Gamma

```{r}
#model call
mod_f <- bf("time_to_true ~ agent * network")
get_prior(mod_f, nltimeto, family = Gamma())

#running the model with regularizing priors 
tttgam_mod <- brm(
  mod_f, 
  family = Gamma(), #or what would be appropriate? 
  prior = c( #& what about priors?
    prior(normal(2, 2), class = "Intercept"),
    prior(normal(0, 2), class = "b"),
    prior(gamma(0.01, 0.01), class = "shape")), #using get_priors. 
  data = nltimeto, 
  cores = 4, iter = 4000, warmup = 2000, chains = 1,
  sample_prior = TRUE #added for later use. 
  #file = "bayes/tttg_mod" #saving for later use - these models take ages to run. 
)

#This is slightly better. 
pp_check(tttgam_mod)
```

three models comparison 

```{r}

#normal 
pp_check(tttn_mod)

#log-normal
pp_check(tttg_mod)

#gamma model
pp_check(tttgam_mod)

```

