---
title: "Untitled"
author: "Victor Møller"
date: "20 maj 2019"
output: html_document
---

updated 09-11-2019.
Still much work to do. 

```{r}

library(pacman)
p_load(readr, tidyverse, ggplot2, RColorBrewer, reshape2, ggthemes,
       viridis, ggridges, ggunchained, rlang)

```

loading data. 

```{r}

#working directory. 
setwd("~/CRUST-1/data/tests")
path = "~/CRUST-1/data/tests/"
files <- list.files(path = path, pattern="*csv")

#taken from the scatter-plot file (reconsider what is needed)
mycols <- c("replica", 
            "turn", 
            "studies", 
            "network", 
            "population", 
            "sigma",
            "sample_size",
            "true_model",
            "strategy",
            "edges_replication_study",
            "edges_replicated",
            "proportion_true",
            "final_global_true_model")

#loading them 
dfList <- lapply(files_100, function(f) {  
   read.csv(paste0(path, f))[mycols]
})

#subsetting (because of computational demands)
small_100 <- do.call(rbind, dfList) 
rm(dfList)
```

```{r}

#reading data (read_csv from readr is much faster than read.csv)
df <- read_csv("mikkelBash.csv")


```



Preprocessing (should also be adjusted to accommodate better early prep). 

```{r}

df <- df %>%
  mutate(network = factor(network), 
         true_model = factor(true_model), 
         base_SS = factor(base_SS))

#combining them 
small$network <- as.factor(small$network)
small$true_model <- as.factor(small$true_model)
small$sample_size <- as.factor(small$sample_size)

#replication rate small world 
small_RR <- small %>%
  group_by(replica, sample_size, network, population, sigma, true_model) %>%
  summarize(RR = sum(edges_replicated) / 
              sum(edges_replication_study)) 

```


raincloud prep

```{r}

#preparing raincloud (can be customized)
raincloud_theme = theme(
text = element_text(size = 10),
axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 16),
axis.text = element_text(size = 14),
axis.text.x = element_text(vjust = 0.5),
legend.title=element_text(size=16),
legend.text=element_text(size=16),
legend.position = "right",
plot.title = element_text(lineheight=.8, face="bold", size = 16),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

```

new directory & loading flatViolin

```{r}
setwd("C:/Users/victm/Dropbox/CogSci 4/Social and Cultural Dynamics in Cognition/exam/CRUST-1")
baseDir <- "."
scriptDir <- paste0(baseDir, "/src/functions")
inputDir <- paste0(baseDir, "/data")
outputDir <- paste0(baseDir, "/data")
source(paste0(scriptDir, "/flatViolin.R"))
```

Raincloud plot.
By inputting total_RR_sig instead we get a plot grouped by sigma & 
thus with 3 times the number of observations. 

```{r}

#raincloud plot
g <- small_RR %>%
  filter(sample_size == "100") %>%
  ggplot(aes(x = population, 
             y = RR, fill = population)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = RR, color = population), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate for populations",
       subtitle = "Sample size: 100",
       x = "Population", 
       y = "Replication rate") + #sets the legend title.
  raincloud_theme

#call the plot
g

```

Raincloud plot by sample size & agent population.
By inputting total_RR_sig instead we get a plot grouped by sigma & 
thus with 3 times the number of observations. 

```{r}
#raincloud plot
g <- ggplot(data = small_RR, aes(x = population, 
                                 y = RR, fill = sample_size)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
  geom_point(aes(y = RR, color = sample_size), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) + #not clear that this changes much. 
  #guides(fill = FALSE) + #legend can be deleted. 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate for populations",
       subtitle = "Grouped by sample size", 
       x = "Population", 
       y = "Replication rate",
       fill = "Sample size") + #sets the legend title.
  raincloud_theme

#call the plot
g
```

trying to group by true model. 

```{r}

#raincloud plot
g <- small_RR %>%
  filter(sample_size == "100") %>%
  ggplot(aes(x = population, 
                              y = RR, fill = true_model)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
  geom_point(aes(y = RR, color = true_model), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) + #not clear that this changes much. 
  #guides(fill = FALSE) + #legend can be deleted. 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate for populations",
       subtitle = "Grouped by true model", 
       x = "Population", 
       y = "Replication rate",
       fill = "True model") + #sets the legend title.
  raincloud_theme

#call the plot
g
```

with RR for true model (preprocessing)
by global

```{r}
#creating the grouped by (3 rows missing)
by_global <- small %>%
  group_by(final_global_true_model, replica, network, population, 
           true_model, sigma, sample_size) %>%
  summarize(RR = sum(edges_replicated) / sum(edges_replication_study)) %>%
  filter(final_global_true_model == 1) 

#adding stuff.  
small_RR <- small_RR %>%
  mutate(final_global_true_model = "Overall") 

#changing stuff
by_global$final_global_true_model <- "True"

#cbinding 
all_overall <- rbind(by_global, small_RR)

#factor. 
all_overall$final_global_true_model <- as.factor(all_overall$final_global_true_model)
```


```{r}

#raincloud plot
g <- all_overall %>%
  filter(sample_size == "100") %>%
  ggplot(aes(x = population, 
                              y = RR, fill = final_global_true_model)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
  geom_point(aes(y = RR, color = final_global_true_model), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) + #not clear that this changes much. 
  #guides(fill = FALSE) + #legend can be deleted. 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate for populations",
       subtitle = "Grouped by true model", 
       x = "Population", 
       y = "Replication rate",
       fill = "Replication rate") + #sets the legend title.
  raincloud_theme

#call the plot
g
```

sigma 100 

```{r}

#sigma as factor
small_RR$sigma <- as.factor(small_RR$sigma)

#raincloud plot
g <- small_RR %>%
  filter(sample_size == "100") %>%
  ggplot(aes(x = population, 
                              y = RR, fill = sigma)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
  geom_point(aes(y = RR, color = sigma), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) + #not clear that this changes much. 
  #guides(fill = FALSE) + #legend can be deleted. 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate by population",
       subtitle = "Sample size: 100", 
       x = "Population", 
       y = "Replication rate",
       fill = "Sigma") + #sets the legend title.
  raincloud_theme

#call the plot
g

```

for sample size 20

```{r}

#raincloud plot
g1 <- small_RR %>%
  filter(sample_size == "20") %>%
  ggplot(aes(x = population, 
                              y = RR, fill = sigma)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
  geom_point(aes(y = RR, color = sigma), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) + #not clear that this changes much. 
  #guides(fill = FALSE) + #legend can be deleted. 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate by population",
       subtitle = "Sample size: 20", 
       x = "Population", 
       y = "Replication rate",
       fill = "Sigma") + #sets the legend title.
  raincloud_theme

#call the plot
g1

library(cowplot)
plot_grid(g, g1)

```

