---
title: "Untitled"
author: "Victor Møller"
date: "20 maj 2019"
output: html_document
---

updated 09-11-2019. 
plots looking at RR & its connection to TAT. 

```{r}

library(pacman)
p_load(readr, tidyverse, ggplot2, RColorBrewer, reshape2, ggthemes,
       viridis, ggridges, ggunchained, rlang)

```

loading data (come back)

```{r}

#working directory. 
setwd("~/CRUST-1/data/tests")
path = "~/CRUST-1/data/tests/"
files <- list.files(path = path, pattern="*csv")

#taken from the scatter-plot file (reconsider what is needed)
mycols <- c("replica", 
            "turn", #need this??
            "studies", 
            "network", 
            "colab_cond",
            "population", 
            "sigma",
            "net_size",
            "base_SS",
            "true_model",
            "strategy",
            "switch_rep_study",
            "switch_rep",
            "prop_true",
            "prop_t_mod") #importantly. 

#loading them 
dfList <- lapply(files, function(f) {  
   read.csv(paste0(path, f))[mycols]
})

#subsetting (because of computational demands)
df <- do.call(rbind, dfList) 
rm(list=setdiff(ls(), "df"))

```

BELOW: 
preprocessing. 
with RR for true model & by global.
why is net_size loaded as "unknown" instead of integer?

```{r}

#replication rate & TAT overall 
RR_TAT <- df %>%
  group_by(replica, network, population, sigma, true_model,
           base_SS, net_size, colab_cond) %>%
  summarize(RR = sum(switch_rep) / sum(switch_rep_study),
            TAT = mean(prop_true)) %>%
  ungroup %>%
  mutate(base_SS = ifelse(base_SS == 20, 
                              "Sample size: 20",
                              "Sample size: 100"))

#replication rate & TAT (for )
#legit to compute TAT for the subset?
RR_TAT_TF <- df %>%
  group_by(prop_t_mod, replica, network, population, sigma, true_model,
           base_SS, net_size, colab_cond) %>%
  summarize(RR = sum(switch_rep) / sum(switch_rep_study),
            TAT = mean(prop_true)) %>%
  ungroup %>%
  mutate(base_SS = ifelse(base_SS == 20,
                              "Sample size: 20",
                              "Sample size: 100"))

#adding stuff (this is overall).
RR_TAT <- RR_TAT %>%
  mutate(prop_t_mod = "Overall") 

#changing stuff (this is true).
RR_TAT_TF$prop_t_mod <- ifelse(RR_TAT_TF$prop_t_mod == "1", "True", "False")

#binding 
RR_TAT_TOTAL <- rbind(RR_TAT, RR_TAT_TF)

#Factorizing & Renaming 
RR_TAT_TOTAL <- RR_TAT_TOTAL %>%
  mutate(prop_t_mod = factor(prop_t_mod), 
         sigma = factor(sigma), 
         true_model = factor(true_model)) %>%
  rename("Population" = "population",
         "Network" = "network",
         "Sigma" = "sigma",
         "TrueModel" = "true_model",
         "SampleSize" = "base_SS",
         "Colaboration" = "colab_cond",
         "ProposedTrue" = "prop_t_mod",
         "NetworkSize" = "net_size")

```

BELOW: 
(overall) Replication rate vs. time at true model. 
This is what we prep. with our melt. 
We also create a function that can be used to plot. 
NB: the text for the plot does note make sense at the moment. 
It will have to be tailored to our needs later when we know what
we want to group based on. 

```{r}

#melting. 
melt_RR_TAT <- melt(RR_TAT_TOTAL, 
                    id.vars = c("replica", "Network", "Population",
                                "Sigma", "TrueModel", "SampleSize",
                                "Colaboration", "ProposedTrue",
                                "NetworkSize"), 
                    measure.vars = c("RR", "TAT"), 
                    variable.name = "variable", 
                    value.name = "proportion")

#for populations: 
RR_TAT_FUN <- function(melted_frame, group_var){

  group_var <- enquo(group_var)

  g <- melted_frame %>%
      filter(ProposedTrue == "Overall", #meaning full replicas. 
             SampleSize == "Sample size: 20") %>%
      ggplot(aes(x = proportion, y = UQ(group_var), 
                               color = variable, fill = variable)) +
      geom_density_ridges(jittered_points = TRUE, scale = 0.8, 
                          rel_min_height = .01,
                          point_shape = "|", point_size = 3, size = 0.25, 
                          position = position_points_jitter(height = 0)) +
      scale_y_discrete(expand = c(0.01, 0)) +
      scale_x_continuous(expand = c(0,0), 
                         name = "Replication rate & time at true model") +
      scale_fill_manual(values = c("#D55E0050", "#0072B250"), 
                        labels = c("Replication rate", "Time at true model")) +
      scale_color_manual(values = c("#D55E00", "#0072B2"), guide = "none") +
      scale_discrete_manual("point_color", values = c("#D55E00", "#0072B2"), 
                            guide = "none") +
      guides(fill = guide_legend("",
        override.aes = list(
        fill = c("#D55E00A0", "#0072B2A0"),
        color = NA, point_color = NA))
      ) +
      theme_ridges(center = TRUE) + 
      theme_janco_point() 
      
    g + labs(caption = "Sample size: 100. 'Replication rate' and 'proportion of time at the true model' both on the x-axis. \n Density curves are averaged over sigma-levels, true models and replicas. \n Lines at the bottom represent mean values for individual replicas") +
      theme(plot.caption = element_text(hjust = 0.5))
}



```

Below: 
plotting with the function RR_TAT_FUN. 

```{r}

colnames(melt_RR_TAT)

RR_TAT_FUN(melt_RR_TAT, Sigma)
RR_TAT_FUN(melt_RR_TAT, Population)
RR_TAT_FUN(melt_RR_TAT, TrueModel)
RR_TAT_FUN(melt_RR_TAT, Network)
RR_TAT_FUN(melt_RR_TAT, Colaboration)

```


Below: 
preparation for plotting of RR of TRUE/FALSE.
NB: the text for the plot is bogus. 

```{r}

#ridges plot
RR_FUN <- function(melted_frame, group_var){
  
  group_var <- enquo(group_var)
  
g1 <- melted_frame %>%
    filter(SampleSize == "Sample size: 20",
           variable == "RR",
           ProposedTrue != "False") %>%
    ggplot(aes(x = proportion, y = UQ(group_var),
               color = ProposedTrue, 
               fill = ProposedTrue)) +
    geom_density_ridges(jittered_points = TRUE, scale = 0.8, rel_min_height = .01,
                        point_shape = "|", point_size = 3, size = 0.25, 
                        position = position_points_jitter(height = 0)) +
    scale_y_discrete(expand = c(0.01, 0)) +
    xlim(0,1) + xlab("Replication rate") +
    scale_fill_manual(values = c("#D55E0050", "#0072B250")) +
    scale_color_manual(values = c("#D55E00", "#0072B2"), guide = "none") +
    scale_discrete_manual("point_color", values = c("#D55E00", "#0072B2"), 
                          guide = "none") +
    guides(fill = guide_legend("",
      override.aes = list(
      fill = c("#D55E00A0", "#0072B2A0"),
      color = NA, point_color = NA))) + 
    theme_ridges(center = TRUE) +
      theme_janco_point() 
    
  g1 + labs(caption = "Sample size: 20. Density curves are averaged over sigma-levels, true models and replicas. \n Lines at the bottom represent mean values for individual replicas") +
    theme(plot.caption = element_text(hjust = 0.5))

}

```

Below:
running the plots of RR

```{r}

#what you can group over
colnames(melt_RR_TAT)

#looking at the plots
RR_FUN(melt_RR_TAT, Network)
RR_FUN(melt_RR_TAT, Population)
RR_FUN(melt_RR_TAT, Sigma)
RR_FUN(melt_RR_TAT, TrueModel)
RR_FUN(melt_RR_TAT, Colaboration)

```

ABOVE: 
We have 13 rows containing non-finite values.
These are replicas of TESS with high sigma for TRUE (I.e., there were no replication attemts of the true model in those runs). Of course this is somewhat problematic as it will skew the results somewhat. However, on aggregate the picture should still be relatively clear. 

BELOW: 
Plotting replication rate (1) overall, (2) false & (3) true. 
This makes some sense (to me) since the overall is what we know from the "outside",
the true we want to have high & the false we want to have low. 

```{r}


#ridges plot
RR_FUN_FALSE <- function(melted_frame, group_var){
  
  group_var <- enquo(group_var)
  
g1 <- melted_frame %>%
    filter(SampleSize == "Sample size: 20",
           variable == "RR") %>%
    ggplot(aes(x = proportion, y = UQ(group_var),
               color = ProposedTrue, 
               fill = ProposedTrue)) +
    geom_density_ridges(jittered_points = TRUE, scale = 0.8, rel_min_height = .01,
                        point_shape = "|", point_size = 3, size = 0.25, 
                        position = position_points_jitter(height = 0)) +
    scale_y_discrete(expand = c(0.01, 0)) +
    xlim(0,1) + xlab("Replication rate") +
    scale_fill_manual(values = c("#16AD3C50", "#D55E0050", "#0072B250")) +
    scale_color_manual(values = c("#16AD3C", "#D55E00", "#0072B2"), 
                       guide = "none") +
    scale_discrete_manual("point_color", 
                          values = c("#16AD3C", "#D55E00", "#0072B2"), 
                          guide = "none") +
    guides(fill = guide_legend("",
      override.aes = list(
      fill = c("#16AD3C50", "#D55E00A0", "#0072B2A0"),
      color = NA, point_color = NA))) + 
    theme_ridges(center = TRUE) +
      theme_janco_point() 
    
  g1 + labs(caption = "Sample size: 20. Density curves are averaged over sigma-levels, true models and replicas. \n Lines at the bottom represent mean values for individual replicas") +
    theme(plot.caption = element_text(hjust = 0.5))

}

```

ABOVE:
consider colours: 
(1) manually here: https://htmlcolorcodes.com/
(2) otherwise consider color brewer package. 

Below:
generating plots. 

```{r}

#what you can group over
colnames(melt_RR_TAT)

#looking at the plots
RR_FUN_FALSE(melt_RR_TAT, Network)
RR_FUN_FALSE(melt_RR_TAT, Population)
RR_FUN_FALSE(melt_RR_TAT, Sigma)
RR_FUN_FALSE(melt_RR_TAT, TrueModel)
RR_FUN_FALSE(melt_RR_TAT, Colaboration)

```

