---
title: "Untitled"
author: "Victor Møller"
date: "20 maj 2019"
output: html_document
---

packages

```{r}
library(pacman)
p_load(readr, tidyverse, ggplot2, RColorBrewer, reshape2, ggthemes)

```

loading data

```{r}
#set working directory
setwd("C:/Users/victm/Dropbox/CogSci 4/Social and Cultural Dynamics in Cognition/exam/CRUST-1/data/rfs50")

#lattice
temp <- list.files(pattern=".csv")

#making work
names(temp) <- list.files(pattern=".csv")
y <- c("lattice_bo_0.2_BIC_100_hard_100.csv",
       "lattice_bo_0.5_BIC_100_hard_100.csv",
       "lattice_bo_0.8_BIC_100_hard_100.csv",
       "lattice_epi_0.2_BIC_100_hard_100.csv",
       "lattice_epi_0.5_BIC_100_hard_100.csv",
       "lattice_epi_0.8_BIC_100_hard_100.csv",
       "lattice_mave_0.2_BIC_100_hard_100.csv",
       "lattice_mave_0.5_BIC_100_hard_100.csv",
       "lattice_mave_0.8_BIC_100_hard_100.csv",
       "lattice_tess_0.2_BIC_100_hard_100.csv",
       "lattice_tess_0.5_BIC_100_hard_100.csv",
       "lattice_tess_0.8_BIC_100_hard_100.csv")
temp1 <- temp[y]
temp1

#loading them 
for(i in 1:length(temp1)) assign(temp1[i], read.csv(temp1[i], sep = ","))

```

putting them together 

```{r}

#rbind them into lattice. 
lattice <- rbind(lattice_bo_0.2_BIC_100_hard_100.csv,
       lattice_bo_0.5_BIC_100_hard_100.csv,
       lattice_bo_0.8_BIC_100_hard_100.csv,
       lattice_epi_0.2_BIC_100_hard_100.csv,
       lattice_epi_0.5_BIC_100_hard_100.csv,
       lattice_epi_0.8_BIC_100_hard_100.csv,
       lattice_mave_0.2_BIC_100_hard_100.csv,
       lattice_mave_0.5_BIC_100_hard_100.csv,
       lattice_mave_0.8_BIC_100_hard_100.csv,
       lattice_tess_0.2_BIC_100_hard_100.csv,
       lattice_tess_0.5_BIC_100_hard_100.csv,
       lattice_tess_0.8_BIC_100_hard_100.csv)

#remove all the old shit 
rm(list=setdiff(ls(), "lattice"))

```

small world 

```{r}

#small world 
temp <- list.files(pattern=".csv")
names(temp) <- list.files(pattern=".csv")
y <- c("small_bo_0.2_BIC_100_hard_100.csv",
       "small_bo_0.5_BIC_100_hard_100.csv", #this is fucked. 
       "small_bo_0.8_BIC_100_hard_100.csv",
       "small_epi_0.2_BIC_100_hard_100.csv",
       "small_epi_0.5_BIC_100_hard_100.csv",
       "small_epi_0.8_BIC_100_hard_100.csv",
       "small_mave_0.2_BIC_100_hard_100.csv",
       "small_mave_0.5_BIC_100_hard_100.csv",
       "small_mave_0.8_BIC_100_hard_100.csv",
       "small_tess_0.2_BIC_100_hard_100.csv",
       "small_tess_0.5_BIC_100_hard_100.csv",
       "small_tess_0.8_BIC_100_hard_100.csv")
temp1 <- temp[y]
temp1

#loading them 
for(i in 1:length(temp1)) assign(temp1[i], read.csv(temp1[i], sep = ","))

```

putting them together 

```{r}

#rbind them into lattice. 
small <- rbind(small_bo_0.2_BIC_100_hard_100.csv,
       small_bo_0.5_BIC_100_hard_100.csv,
       small_bo_0.8_BIC_100_hard_100.csv,
       small_epi_0.2_BIC_100_hard_100.csv,
       small_epi_0.5_BIC_100_hard_100.csv,
       small_epi_0.8_BIC_100_hard_100.csv,
       small_mave_0.2_BIC_100_hard_100.csv,
       small_mave_0.5_BIC_100_hard_100.csv,
       small_mave_0.8_BIC_100_hard_100.csv,
       small_tess_0.2_BIC_100_hard_100.csv,
       small_tess_0.5_BIC_100_hard_100.csv,
       small_tess_0.8_BIC_100_hard_100.csv)

#remove all the old shit 
rm(list= ls()[!(ls() %in% c('lattice','small'))])
```

grouping for plotting 

```{r}

#relevant subset 
lattice_sub <- lattice %>%
  subset(tried >= 1)

small_sub <- small %>%
  subset(tried >= 1)

#replication rate lattice
lattice_RR <- lattice_sub %>%
  group_by(replica, network, population) %>%
  summarize(replicated = sum(replicated) / sum(not_replicated + replicated)) 

#replication rate small world 
small_RR <- small_sub %>%
  group_by(replica, network, population) %>%
  summarize(replicated = sum(replicated) / sum(not_replicated + replicated)) 

#combining them 
total_RR <- rbind(lattice_RR, small_RR)
total_RR$network <- as.factor(total_RR$network)

```

grouping or plotting (with sigma). 

```{r}

#replication rate lattice
lattice_RR_sig <- lattice_sub %>%
  group_by(replica, network, population, sigma) %>%
  summarize(replicated = sum(replicated) / sum(not_replicated + replicated)) 

#replication rate small world 
small_RR_sig <- small_sub %>%
  group_by(replica, network, population, sigma) %>%
  summarize(replicated = sum(replicated) / sum(not_replicated + replicated)) 

#combining them 
total_RR_sig <- rbind(lattice_RR_sig, small_RR_sig)
total_RR$network <- as.factor(total_RR$network)

```

raincloud prep

```{r}

#preparing raincloud (can be customized)
raincloud_theme = theme(
text = element_text(size = 10),
axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 16),
axis.text = element_text(size = 14),
axis.text.x = element_text(vjust = 0.5),
legend.title=element_text(size=16),
legend.text=element_text(size=16),
legend.position = "right",
plot.title = element_text(lineheight=.8, face="bold", size = 16),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

```

making ready for plotting 

```{r}
setwd("C:/Users/victm/Dropbox/CogSci 4/Social and Cultural Dynamics in Cognition/exam/CRUST-1")
baseDir <- "."
scriptDir <- paste0(baseDir, "/src/functions")
inputDir <- paste0(baseDir, "/data")
outputDir <- paste0(baseDir, "/data")
source(paste0(scriptDir, "/flatViolin.R"))
```

Raincloud plot.
By inputting total_RR_sig instead we get a plot grouped by sigma & 
thus with 3 times the number of observations. 

```{r}

#raincloud plot
g <- ggplot(data = total_RR_sig, aes(x = population, 
                                 y = replicated, fill = population)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(aes(y = replicated, color = population), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate for populations",
       subtitle = "Violin = summarized, iterations avg. over sigma = points", 
       x = "Population", 
       y = "Replication rate") + #sets the legend title.
  raincloud_theme

#call the plot
g

```

Raincloud plot by network type & agent population.
By inputting total_RR_sig instead we get a plot grouped by sigma & 
thus with 3 times the number of observations. 

```{r}
#raincloud plot
g <- ggplot(data = total_RR_sig, aes(x = population, 
                                 y = replicated, fill = network)) +
  geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .7) +
  geom_point(aes(y = replicated, color = network), 
                  position = position_jitter(width = .15), 
                  size = .5, alpha = 0.8) +
  geom_boxplot(width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 2) + #not clear that this changes much. 
  #guides(fill = FALSE) + #legend can be deleted. 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate for populations",
       subtitle = "Violin = summarized, iterations avg. over sigma = points", 
       x = "Population", 
       y = "Replication rate") + #sets the legend title.
  raincloud_theme

#call the plot
g
```

specifying manually from different dataframes. 

```{r}

#raincloud plot
g <- ggplot() +
  geom_flat_violin(data = small_RR, 
                   aes(x = population, y = replicated, fill = population),
                   position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_flat_violin(data = lattice_RR, 
                   aes(x = population, y = replicated, fill = population),
                   position = position_nudge(x = .2, y = 0), alpha = .8) +
  geom_point(data = small_RR, 
             aes(x = population, y = replicated, color = population),
             position = position_jitter(width = .15), 
             size = .5, alpha = 0.8) +
  geom_point(data = lattice_RR, 
             aes(x = population, y = replicated, color = population),
             position = position_jitter(width = .15), 
             size = .5, alpha = 0.8) +
  geom_point(data = small_RR,
             aes(x = population, y = replicated, color = population), 
             position = position_jitter(width = .15), 
             size = .5, alpha = 0.8) +
  geom_boxplot(data = small_RR, 
               aes(x = population, y = replicated, fill = population),
               width = .1, outlier.shape = NA, alpha = 0.5) +
    geom_boxplot(data = lattice_RR, 
               aes(x = population, y = replicated, fill = population),
               width = .1, outlier.shape = NA, alpha = 0.5) +
  expand_limits(x = 3) +
  guides(fill = FALSE) + 
  guides(color = FALSE) +
  scale_fill_tableau() +
  scale_color_tableau() +
  #coord_flip() +
  theme_bw() +
  labs(title = "Replication rate for populations & network types",
       subtitle = "Violin = summarized, iterations avg. over sigma = points", 
       x = "Population", 
       y = "Replication rate") + #sets the legend title.
  raincloud_theme

#call the plot
g

```

